---
title: "test"
author: "Fabian Scheifele"
date: "2022-12-19"
output: html_document
editor_options: 
  chunk_output_type: console
---

1. load relevant Packages
```{r setup, include=FALSE}
suppressMessages(memory.limit(size = NA))

if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}

suppressMessages(install_load("tidyverse", "dplyr", "ggplot2", "readr", "readxl","knitr","here", "tidyverse" , "anytime" , "data.table", "corrplot", "naniar", "fuzzyjoin","expss", "janitor","readr", "data.table", "labelled", "countrycode","grep", "economiccomplexity","xtable","ggbump", "cowplot","ggrepel", "survival", "basedosdados", "bigrquery"))


`%notin%` <- Negate(`%in%`)
```

2. load raw datasets
```{r}
aneel_generation<-fread(here("raw","siga-empreendimentos-geracao.csv"), sep = ';', encoding = "Latin-1")
auction_file<-fread(here("raw","resultado-leiloes-geracao.csv"), sep = ';', encoding = "Latin-1")
municipality_id<-readRDS(here("raw","geodata_municipios.RDS"))

operators<-read.csv(here("raw","agentes-geracao-energia-eletrica.csv"), sep = ';', encoding = "latin1")%>%select(2,3,4,7,8)
```

3. Merge operator names with plant-level data (better merge long than wide)
```{r}
#left join the data
aneel_generation<-aneel_generation%>%left_join(operators, by=c("IdeNucleoCEG"))

#2 removing duplicate plants (due to different contract types for the same plant)

distinct<-aneel_generation%>%distinct(IdeNucleoCEG, NomAgente)
duplicated<-aneel_generation%>%group_by(IdeNucleoCEG, NomAgente)%>%mutate(no=n())

aneel_generation <- aneel_generation %>%
  distinct(IdeNucleoCEG, NomAgente, .keep_all = TRUE) %>%
  mutate(exploitation_regime = case_when(
    str_detect(DscPropriRegimePariticipacao, "(PIE)") ~ "IPP", 
    str_detect(DscPropriRegimePariticipacao, "(SP)") ~ "Public Service", 
    str_detect(DscPropriRegimePariticipacao, "(APE)") ~ "Self-producer", 
    str_detect(DscPropriRegimePariticipacao, "(REG)") ~ "registered (<=5MW)",
    TRUE ~ NA_character_
  ))

na_regime<-aneel_generation%>%filter(is.na(exploitation_regime))    
    
aneel_generation <- aneel_generation %>%select(-DscPropriRegimePariticipacao)
remove(duplicated)
```


4. Clean Generation files to get ready for merge
```{r}
aneel_generation$year_operation<-substr(aneel_generation$DatEntradaOperacao,1,4)
aneel_generation$year_operation<-as.numeric(aneel_generation$year_operation)

#To have year-ending panel take only until 2022 (newest data will have some 2023 values)
aneel_generation<-aneel_generation%>%filter(year_operation<=2022)

#Separate the DScMunicipalities variable  here
aneel_generation <- aneel_generation %>% separate(DscMuninicpios, into = c('DscMuninicpios', 'DscMuninicpios_2', 'DscMuninicpios_3',
                                                                           'DscMuninicpios_4', 'DscMuninicpios_5', 'DscMuninicpios_6'), sep = ",")

#Bring the municipality names into long format
aneel_generation<-pivot_longer(aneel_generation, cols = c('DscMuninicpios', 'DscMuninicpios_2', 'DscMuninicpios_3',
                                                                           'DscMuninicpios_4', 'DscMuninicpios_5', 'DscMuninicpios_6'), 
                               names_to = "wide_var", values_to = "municipality")
aneel_generation<-aneel_generation%>%filter(!is.na(municipality))%>%select(-wide_var)

distinct<-aneel_generation%>%distinct(municipality,IdeNucleoCEG, NomAgente)
remove(distinct)


```

5. Merge auction and generation (first order and take distinct generation units)
```{r}
#First check auction file for multiple auctions per IdeNucleoCEG and keep only the first auction participation
auction_file<-auction_file%>%arrange(IdeNucleoCEG, DatLeilao)
duplicates<-auction_file%>%
  group_by(IdeNucleoCEG)%>%
  mutate(no_auction=n_distinct(NumLeilao))%>%filter(no_auction>1)%>%
  select(DatLeilao, NumLeilao, IdeNucleoCEG,no_auction)


auction_file_distinct<-auction_file%>%distinct(IdeNucleoCEG, .keep_all=TRUE)%>%select(2,4,9,26)
auction_generation<-left_join(aneel_generation, auction_file_distinct, by='IdeNucleoCEG')%>%
  mutate(auction=case_when(!is.na(AnoLeilao)~1, TRUE~0))


remove(duplicates)
remove(distinct)
remove(auction_file_distinct)
remove(aneel_generation)

#remove irrelavant columns
auction_generation<-auction_generation%>%select(-CodCEG,-DatGeracaoConjuntoDados,-DscSubBacia, -DscFonteCombustivel,-NomFonteCombustivel,-DscTipoOutorga,-IdcGeracaoQualificada)%>%
  rename(mw_authorized=MdaPotenciaOutorgadaKw)%>%
  rename(mw_operation=MdaPotenciaFiscalizadaKw)%>%
  rename(mw_assured=MdaGarantiaFisicaKw)%>%rename(lat=NumCoordNEmpreendimento)%>%
  rename(lon=NumCoordEEmpreendimento)%>%
  rename(startdate_concession=DatInicioVigencia)%>%
  rename(enddate_concession=DatFimVigencia)

#change variable names and clean
auction_generation$mw_authorized<- as.numeric(gsub(",", ".",auction_generation$mw_authorized))
auction_generation$mw_operation<- as.numeric(gsub(",", ".",auction_generation$mw_operation))  
auction_generation$mw_assured<- as.numeric(gsub(",", ".",auction_generation$mw_assured))  
auction_generation$PctParticipacao<- as.numeric(gsub(",", ".",auction_generation$PctParticipacao)) 

auction_generation<-auction_generation%>%
  mutate(mw_authorized=(mw_authorized/1000))%>%
  mutate(mw_operation=(mw_operation/1000))%>%
  mutate(mw_assured=(mw_assured/1000))
  
auction_generation$lon<- as.numeric(gsub(",", ".",auction_generation$lon))
auction_generation$lat<- as.numeric(gsub(",", ".",auction_generation$lat))  
```


6. merge municipality information with ANEEL data (from Step 4)
```{r}
municipality_id$municipality <- paste(municipality_id$nome_municipio, " - ", municipality_id$sigla_uf)

#create row_id to be able to group later
auction_generation<- auction_generation%>%mutate(id=row_number())
auction_generation$municipality<-str_trim(auction_generation$municipality)
municipality_id$municipality<-str_trim(municipality_id$municipality)



#Correct individual entries to be found
auction_generation$municipality[auction_generation$id==233]<-"São Gabriel da Cachoeira - AM"

matchDistance <- stringdist_join(
                  auction_generation, municipality_id,
                   by           = "municipality",
                   mode         = "left",
                   ignore_case  = TRUE, 
                   method       = "jw", 
                   max_dist     = 0.15,
                  distance_col = "dist")

#when selecting matches you have to group by Plant ID because you want to keep all plants
auction_generation_final <-matchDistance%>%
                group_by(id) %>%
                slice_min(dist,n=1, with_ties = FALSE)

quality_check<-auction_generation_final%>%select(municipality.x, municipality.y, dist,lon,lat,geometria )

#new municipality thats why not found

sum(is.na(auction_generation_final$id_municipio))


nas<-auction_generation_final%>%
  filter(is.na(id_municipio))%>%
  select(id_municipio, SigUFPrincipal, municipality.x, municipality.y, lon,lat)

#manual because tolerance cannot be increased
auction_generation_final$municipality.x[auction_generation_final$id==1252]<-"Lagoa de Itaenga - PB"
auction_generation_final$municipality.y[auction_generation_final$id==1252]<-"Lagoa de Itaenga - PB"
auction_generation_final$id_municipio[auction_generation_final$id==1252]<-2608503

auction_generation_final$municipality.x[auction_generation_final$id==1810]<-"Lagoa de Itaenga - PB"
auction_generation_final$municipality.y[auction_generation_final$id==1810]<-"Lagoa de Itaenga - PB"
auction_generation_final$id_municipio[auction_generation_final$id==1810]<-2608503

auction_generation_final$id_municipio[auction_generation_final$id==2714]<-3520905
auction_generation_final$municipality.x[auction_generation_final$id==2714]<-"Ipaussu - SP"
auction_generation_final$municipality.y[auction_generation_final$id==2714]<-"Ipaussu - SP"

auction_generation_final$municipality.x[auction_generation_final$id==3205]<-"Sete Lagoas - MG"
auction_generation_final$municipality.y[auction_generation_final$id==3205]<-"Sete Lagoas - MG"
auction_generation_final$id_municipio[auction_generation_final$id==3205]<-3167202


auction_generation_final$municipality.x[auction_generation_final$id==3545]<-"Moji Mirim - SP"
auction_generation_final$municipality.x[auction_generation_final$id==3545]<-"Moji Mirim - SP"
auction_generation_final$id_municipio[auction_generation_final$id==3545]<-3530805

auction_generation_final$municipality.x[auction_generation_final$id==23809]<-"Floriano - PI"
auction_generation_final$municipality.y[auction_generation_final$id==23809]<-"Floriano - PI"
auction_generation_final$id_municipio[auction_generation_final$id==23809]<-2203909

auction_generation_final$id_municipio[auction_generation_final$id==6099]<-5006275
auction_generation_final$municipality.y[auction_generation_final$id==6099]<-"Paraíso das Águas - MS"

sum(is.na(auction_generation_final$id_municipio))
#no more NAs
remove(matchDistance)
remove(nas)
remove(quality_check)
```

7.Column renaming from Portuguese to English and saving the intermediate file
```{r}
#colomn renaming to English
auction_generation_final <- auction_generation_final%>%select(-DscRegimeExploracao)
auction_generation_final <- auction_generation_final %>%
  rename(
    station_name = 1,
    plant_id = 2,
    generation_type = 4,
    plant_phase = 5,
    fuel_source = 6,
    operation_start_date = 7 ,
    agent_name = 16,
    participation = 17,
    exploitation_regime = 18,
    auction_year = 21,
    auction_number = 22,
    winnig_company = 23,
    mun_id = 26,
    mun_name = 27,
    state = 28
  )

#save clean aneel generation file without bndes info
saveRDS(auction_generation_final, here("intermediate","aneel_generation_nobndes.RDS"))
```

