---
title: "TWFE Estimation"
author: "Fabian Scheifele"
date: "2023-05-17"
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r }
if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}
suppressMessages(install_load("tidyverse", "dplyr", "ggplot2", "readr", "readxl","here","bacondecomp", "fixest", "plm","geobr","sf","ggdist","ggspatial", "ggsn","extrafont","data.table","geosphere"))


theme_set(theme_minimal(base_family = "Times New Roman"))
```

load data
```{r pressure, echo=FALSE}
wind_matched_final_monthly<-readRDS(here("final","wind1to1_final_monthly.RDS"))%>%
  mutate(wind_jobs_endmonth=wind_inst_endmonth+wind_comp_endmonth+wind_om_endmonth)%>%
  mutate(wind_other_jobs_endmonth=total_endmonth-wind_jobs_endmonth)

solar_matched_final_monthly<-readRDS(here("final","solar1to1_final_monthly.RDS"))%>%arrange(id_municipio, ano, month)%>%
  group_by(id_municipio)%>%
  mutate(solar_jobs_endmonth=solar_inst_endmonth+solar_comp_endmonth+solar_om_endmonth)%>%
  mutate(solar_other_jobs_endmonth=total_endmonth-solar_jobs_endmonth)

wind_matched_final_annual<-readRDS(here("final","wind1to1_final_annual.RDS"))
solar_matched_final_annual<-readRDS(here("final","solar1to1_final_annual.RDS"))

# load unmatched data and re-create the treatment variable used for eligibility (prior to matching)
monthly_panel<-readRDS(here("final","monthly_final_noweights.RDS"))
monthly_panel <- monthly_panel %>%
  group_by(id_municipio) %>%
  mutate(solar_treat_prematch = if_else(any(new_mw_solar > 5), 1, 
                                        if_else(any(plant_5MW_distance > 50), 0, NA_integer_))) %>%
  mutate(wind_treat_prematch = if_else(any(new_mw_wind > 5), 1, 
                                       if_else(any(plant_5MW_distance > 50), 0, NA_integer_)))%>%
  mutate(solar_jobs_endmonth=solar_inst_endmonth+solar_comp_endmonth+solar_om_endmonth)%>%
  mutate(solar_other_jobs_endmonth=total_endmonth-solar_jobs_endmonth)%>%
  mutate(wind_jobs_endmonth=wind_inst_endmonth+wind_comp_endmonth+wind_om_endmonth)%>%
  mutate(wind_other_jobs_endmonth=total_endmonth-wind_jobs_endmonth)

unmatched_solar_monthly<-monthly_panel%>%filter(!is.na(solar_treat_prematch))
unmatched_wind_monthly<-monthly_panel%>%filter(!is.na(wind_treat_prematch))

annual_panel<-readRDS(here("final","annual_panel_final_noweights.RDS"))
annual_panel <- annual_panel %>%
  group_by(id_municipio) %>%
  mutate(solar_treat_prematch = if_else(any(new_mw_solar > 5), 1, 
                                        if_else(any(plant_5MW_distance > 50), 0, NA_integer_))) %>%
  mutate(wind_treat_prematch = if_else(any(new_mw_wind > 5), 1, 
                                       if_else(any(plant_5MW_distance > 50), 0, NA_integer_)))

unmatched_solar_annual<-annual_panel%>%filter(!is.na(solar_treat_prematch))
unmatched_wind_annual<-annual_panel%>%filter(!is.na(wind_treat_prematch))
```


Monthly solar 
```{r}
monthly_coefplot_solar <- function(dv, df_origin, t_start, t_max, graph_t_min, graph_t_max, graph_title) {
  formula_string <- paste(dv, "~ d_solar_pre37_bin+ d_solar_pre.[", t_start, ":1] + new_mw_solar + d_solar_post.[1:", t_max, "] +d_solar_post25_bin| id_municipio + month^ano")
  form <- as.formula(formula_string)
  
  fe <- feols(form, df_origin, cluster = "id_municipio")
  
solar_vars <- c("d_solar_pre[0-9]", "d_solar_post[0-9]", "new_mw_solar")
   
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")

  coef <- coef(fe)[grepl(paste0("^(", paste(solar_vars, collapse = "|"), ")"), names(coef(fe)))]
  se <- se(fe)[grepl(paste0("^(", paste(solar_vars, collapse = "|"), ")"), names(coef(fe)))]
  df <- data.frame(coef, se) 
  df<-df%>% mutate(x.axis = c(-37,seq(-35, 25, 1)))
    #add the zero coefficient for -36 (comparison time unit)
  add_row <- data.frame(coef = 0, se = 0, x.axis = -36)
  df <- rbind(df, add_row)
  
  plots <- ggplot(df, aes(x = x.axis, y = coef)) +
    geom_ribbon(aes(ymin = coef - 1.96 * se, ymax = coef + 1.96 * se), fill = "gray70") +
    geom_line() +
    ggtitle(graph_title) +
    labs(x = "", y = "") +
    theme_bw() +
    theme(text = element_text(size = 7)) +
    scale_x_continuous(breaks = c(-37,seq(graph_t_min+4, graph_t_max-4, 4),25),labels=c(paste("-37+"),seq(graph_t_min+4, graph_t_max-4, 4),paste("25+")),expand=c(0.01,0.01)) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = 0, linetype = "dashed")

  ggsave(filename = here("output", "regressions", "TWFE 1-to-1 binning", "solar", paste0(dv, ".png")), 
         plot = plots, 
         units = "px", width = 2000, height = 1000)
  return(plots)
}

A<-monthly_coefplot_solar("solar_inst_endmonth", monthly_panel,35,24,-36,24,"a. Installation")
B<-monthly_coefplot_solar("solar_om_endmonth", monthly_panel, 35,24,-36,24,"b. O&M")
C<-monthly_coefplot_solar("solar_comp_endmonth", monthly_panel, 35,24,-36,24,"c. Components")
D<-monthly_coefplot_solar("solar_other_jobs_endmonth", monthly_panel, 35,24,-36,24,"d. Non-solar sectors")
E<-monthly_coefplot_solar("avg_wage_2020BRL", monthly_panel, 35,24,-36,24,"Wages")
G<-monthly_coefplot_solar("solar_wage_2020BRL", monthly_panel, 35,24,-36,24,"a. Solar: Wages")
solar_firms<-monthly_coefplot_solar("no_establishments_solar", monthly_panel, 35,24,-36,24,"a. Solar: Sector firms")
H<-monthly_coefplot_solar("tertiary_endmonth", monthly_panel, 35,24,-36,24,"c. Tertiary-educated")
I<-monthly_coefplot_solar("secondary_endmonth", monthly_panel, 35,24,-36,24,"b. Secondary-educated")
J<-monthly_coefplot_solar("primary_endmonth", monthly_panel, 35,24,-36,24,"a. Primary-educated")
monthly_coefplot_solar("solar_jobs_endmonth", monthly_panel, 35,24,-36,24,"Solar Jobs")
monthly_coefplot_solar("avg_skill_solar", monthly_panel, 35,24,-36,24,"a. Solar: Skill level")
solar_outside_a<-monthly_coefplot_solar("solar_jobs_outside_endmonth", monthly_panel, 35,24,-36,24,"a. Solar: Sector-specific")
solar_outside_b<-monthly_coefplot_solar("jobs_outside_endmonth", monthly_panel, 35,24,-36,24,"b.Solar: Total")
H_2<-monthly_coefplot_solar("solar_tertiary_endmonth", monthly_panel, 35,24,-36,24,"a. Tertiary-educated")
I_2<-monthly_coefplot_solar("solar_secondary_endmonth", monthly_panel, 35,24,-36,24,"b. Secondary-educated")
J_2<-monthly_coefplot_solar("solar_primary_endmonth", monthly_panel, 35,24,-36,24,"c. Primary-educated")
solar_total_firms<-monthly_coefplot_solar("no_establishments_cnpj", monthly_panel, 35,24,-36,24,"b. Solar: Total firms")


library(patchwork)
solar2x2<- A + B + C + D
ggsave(solar2x2, filename=here("output","regressions","TWFE 1-to-1 binning", "final figures","appendix","solar2x2_unmatched.png"),units="px", width = 2000, height=1000)

#Retrieve no. of observations
solar_unm<- feols(solar_inst_endmonth ~ d_solar_pre37_bin+d_solar_pre.[35:1] + new_mw_solar+ d_solar_post.[1:24]+d_solar_post25_bin |id_municipio + month^ano, monthly_panel, cluster = "id_municipio")
summary(solar_unm)


```


Wind TWFE
```{r}
monthly_coefplot_wind <- function(dv, df_origin, t_start, t_max, graph_t_min, graph_t_max, graph_title) {
  formula_string <- paste(dv, "~ d_wind_pre37_bin+ d_wind_pre.[", t_start, ":1] + new_mw_wind + d_wind_post.[1:", t_max, "] +d_wind_post25_bin| id_municipio + month^ano")
  form <- as.formula(formula_string)
  
  fe <- feols(form, df_origin, cluster = "id_municipio")
  
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")
   
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")

  coef <- coef(fe)[grepl(paste0("^(", paste(wind_vars, collapse = "|"), ")"), names(coef(fe)))]
  se <- se(fe)[grepl(paste0("^(", paste(wind_vars, collapse = "|"), ")"), names(coef(fe)))]
  df <- data.frame(coef, se) 
  df<-df%>% mutate(x.axis = c(-37,seq(-35, 25, 1)))
    #add the zero coefficient for -36 (comparison time unit)
  add_row <- data.frame(coef = 0, se = 0, x.axis = -36)
  df <- rbind(df, add_row)
  
  plots <- ggplot(df, aes(x = x.axis, y = coef)) +
    geom_ribbon(aes(ymin = coef - 1.96 * se, ymax = coef + 1.96 * se), fill = "gray70") +
    geom_line() +
    ggtitle(graph_title) +
    labs(x = "", y = "") +
    theme_bw() +
    theme(text = element_text(size = 7)) +
    scale_x_continuous(breaks = c(-37,seq(graph_t_min+4, graph_t_max-4, 4),25),labels=c(paste("-37+"),seq(graph_t_min+4, graph_t_max-4, 4),paste("25+")),expand=c(0.01,0.01)) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = 0, linetype = "dashed")

  ggsave(filename = here("output", "regressions", "TWFE 1-to-1 binning", "wind", paste0(dv, ".png")), 
         plot = plots, 
         units = "px", width = 2000, height = 1000)
  return(plots)
}

A<-monthly_coefplot_wind("wind_inst_endmonth", monthly_panel,35,24,-36,24,"a. Installation")
B<-monthly_coefplot_wind("wind_om_endmonth", monthly_panel, 35,24,-36,24,"b. O&M")
C<-monthly_coefplot_wind("wind_comp_endmonth", monthly_panel, 35,24,-36,24,"c. Components")
D<-monthly_coefplot_wind("wind_other_jobs_endmonth", monthly_panel, 35,24,-36,24,"d. Non-wind sectors")
E<-monthly_coefplot_wind("avg_wage_2020BRL", monthly_panel, 35,24,-36,24,"Wages")
G<-monthly_coefplot_wind("wind_wage_2020BRL", monthly_panel, 35,24,-36,24,"a. wind: Wages")
wind_firms<-monthly_coefplot_wind("no_establishments_wind", monthly_panel, 35,24,-36,24,"a. wind: Sector firms")
H<-monthly_coefplot_wind("tertiary_endmonth", monthly_panel, 35,24,-36,24,"c. Tertiary-educated")
I<-monthly_coefplot_wind("secondary_endmonth", monthly_panel, 35,24,-36,24,"b. Secondary-educated")
J<-monthly_coefplot_wind("primary_endmonth", monthly_panel, 35,24,-36,24,"a. Primary-educated")
monthly_coefplot_wind("wind_jobs_endmonth", monthly_panel, 35,24,-36,24,"wind Jobs")
monthly_coefplot_wind("avg_skill_wind", monthly_panel, 35,24,-36,24,"a. wind: Skill level")
wind_outside_a<-monthly_coefplot_wind("wind_jobs_outside_endmonth", monthly_panel, 35,24,-36,24,"a. wind: Sector-specific")
wind_outside_b<-monthly_coefplot_wind("jobs_outside_endmonth", monthly_panel, 35,24,-36,24,"b.wind: Total")
H_2<-monthly_coefplot_wind("wind_tertiary_endmonth", monthly_panel, 35,24,-36,24,"a. Tertiary-educated")
I_2<-monthly_coefplot_wind("wind_secondary_endmonth", monthly_panel, 35,24,-36,24,"b. Secondary-educated")
J_2<-monthly_coefplot_wind("wind_primary_endmonth", monthly_panel, 35,24,-36,24,"c. Primary-educated")
wind_total_firms<-monthly_coefplot_wind("no_establishments_cnpj", monthly_panel, 35,24,-36,24,"b. wind: Total firms")


library(patchwork)
wind2x2<- A + B + C + D
ggsave(wind2x2, filename=here("output","regressions","TWFE 1-to-1 binning", "final figures","appendix","wind2x2_unmatched.png"),units="px", width = 2000, height=1000)

#Retrieve no. of observations
wind_unm<- feols(wind_inst_endmonth ~ d_wind_pre37_bin+d_wind_pre.[35:1] + new_mw_wind+ d_wind_post.[1:24]+d_wind_post25_bin |id_municipio + month^ano, monthly_panel, cluster = "id_municipio")
summary(wind_unm)

```


Solar: Repeat with annual data
```{r}
options(scipen=999)
annual_coefplot_solar <- function(dv, df_origin, t_start, t_max, graph_t_min, graph_t_max, graph_title) {
  formula_string <- paste(dv, "~ d_solar_pre7_bin+ d_solar_pre.[", t_start, ":4] +d_solar_pre.[2:1]+ new_mw_solar + d_solar_post.[1:", t_max, "] +d_solar_post4_bin| id_municipio + ano")
  form <- as.formula(formula_string)
  
  fe <- feols(form, df_origin, cluster = "id_municipio")
  
solar_vars <- c("d_solar_pre[0-9]", "d_solar_post[0-9]", "new_mw_solar")
   
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")

  coef <- coef(fe)[grepl(paste0("^(", paste(solar_vars, collapse = "|"), ")"), names(coef(fe)))]
  se <- se(fe)[grepl(paste0("^(", paste(solar_vars, collapse = "|"), ")"), names(coef(fe)))]
  df <- data.frame(coef, se) 
  df<-df%>% mutate(x.axis = c(seq(graph_t_min, -4, 1),seq(-2,graph_t_max,1)))
    #add the zero coefficient for -24 (comparison time unit)
  add_row <- data.frame(coef = 0, se = 0, x.axis = -3)
  df <- rbind(df, add_row)
  
  plots <- ggplot(df, aes(x = x.axis, y = coef)) +
    geom_ribbon(aes(ymin = coef - 1.96 * se, ymax = coef + 1.96 * se), fill = "gray70") +
    geom_line() +
    ggtitle(graph_title) +
    labs(x = "", y = "") +
    theme_bw() +
    theme(text = element_text(size = 7)) +
    scale_x_continuous(breaks = seq(graph_t_min, graph_t_max, 1), 
                       labels = c(paste0(graph_t_min,"+"),seq(graph_t_min+1,graph_t_max-1,1),paste0(graph_t_max,"+"))) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = 0, linetype = "dashed")

  ggsave(filename = here("output", "regressions", "TWFE 1-to-1 binning", "solar", paste0(dv, ".png")), 
         plot = plots, 
         units = "px", width = 2000, height = 1000)
  return(plots)
}

gdp_solar<-annual_coefplot_solar("pib_clean_constant2020_BRL", annual_panel, 6,2,-7,3,"a. Solar")
receipts_solar<-annual_coefplot_solar("total_receipt_BRL2020", annual_panel, 6,2,-7,3,"a. Total Public Receipts")
spending_solar<-annual_coefplot_solar("total_spending", annual_panel, 6,2,-7,3,"a. Solar: Total Public Spending")
```

wind: Repeat with annual data
```{r}
unmatched_wind_annual<-unmatched_wind_annual%>%mutate(infra_spending=spending_infra+spending_energy)
annual_coefplot_wind <- function(dv, df_origin, t_start, t_max, graph_t_min, graph_t_max, graph_title) {
  formula_string <- paste(dv, "~ d_wind_pre7_bin+ d_wind_pre.[", t_start, ":4] +d_wind_pre.[2:1]+ new_mw_wind + d_wind_post.[1:", t_max, "] +d_wind_post6_bin| id_municipio + ano")
  form <- as.formula(formula_string)
  
  fe <- feols(form, df_origin, cluster = "id_municipio")
  
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")
   
wind_vars <- c("d_wind_pre[0-9]", "d_wind_post[0-9]", "new_mw_wind")

  coef <- coef(fe)[grepl(paste0("^(", paste(wind_vars, collapse = "|"), ")"), names(coef(fe)))]
  se <- se(fe)[grepl(paste0("^(", paste(wind_vars, collapse = "|"), ")"), names(coef(fe)))]
  df <- data.frame(coef, se) 
  df<-df%>% mutate(x.axis = c(seq(graph_t_min, -4, 1),seq(-2,graph_t_max,1)))
    #add the zero coefficient for -24 (comparison time unit)
  add_row <- data.frame(coef = 0, se = 0, x.axis = -3)
  df <- rbind(df, add_row)
  
  plots <- ggplot(df, aes(x = x.axis, y = coef)) +
    geom_ribbon(aes(ymin = coef - 1.96 * se, ymax = coef + 1.96 * se), fill = "gray70") +
    geom_line() +
    ggtitle(graph_title) +
    labs(x = "", y = "") +
    theme_bw() +
    theme(text = element_text(size = 7)) +
    scale_x_continuous(breaks = seq(graph_t_min, graph_t_max, 1), 
                       labels = c(paste0(graph_t_min,"+"),seq(graph_t_min+1,graph_t_max-1,1),paste0(graph_t_max,"+"))) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    geom_hline(yintercept = 0, linetype = "dashed")

  ggsave(filename = here("output", "regressions", "TWFE 1-to-1 binning", "wind", paste0(dv, ".png")), 
         plot = plots, 
         units = "px", width = 2000, height = 1000)
  return(plots)
}



gdp_wind<-annual_coefplot_wind("pib_clean_constant2020_BRL", annual_panel, 6,4,-7,5,"b. Wind")

receipts_wind<-annual_coefplot_wind("total_receipt_BRL2020", annual_panel, 6,4,-7,5,"a. Total Public Receipts")
spending_wind<-annual_coefplot_wind("total_spending", annual_panel, 6,4,-7,5,"a. Total Public Spending")

receipts__all<-receipts_solar+receipts_wind
ggsave(receipts__all, filename=here("output","regressions","TWFE 1-to-1 binning", "final figures","appendix","receipts_wind_unmatched.png"),units="px", width = 2000, height=2000)

gdp_both<-gdp_solar+gdp_wind
ggsave(gdp_both, filename=here("output","regressions","TWFE 1-to-1 binning", "final figures","appendix","gdp_unmatched.png"),units="px", width = 2000, height=1000)

annual_obs <- feols(pib_clean_constant2020_BRL ~ d_solar_pre.[7:1] + new_mw_solar+ d_solar_post.[1:3] |id_municipio + ano, annual_panel)
summary(annual_obs)
```


Wind Robustness: Leave-one-out estimation of total employment (always leaving one subgroup out)
```{r}
# Get unique values of subclass_wind
unique_subclass_wind <- unique(wind_matched_final_monthly$subclass_wind)

# Initialize an empty dataframe to store coefficients
coefficients_df <- data.frame()
se_df <- data.frame()
# Loop over unique values of subclass_wind and run regression
for (i in unique_subclass_wind) {
    # Filter out the current value of subclass_wind
    filtered_data <- wind_matched_final_monthly[wind_matched_final_monthly$subclass_wind != i, ]
    
    
    # Run the regression
    wind_total_form <- xpd(wind_jobs_endmonth ~ d_wind_pre37_bin+ d_wind_pre.[35:1] + new_mw_wind + d_wind_post.[1:24] + d_wind_post25_bin | id_municipio + month^ano)
    wind_total_fe <- feols(wind_total_form, filtered_data, cluster = "id_municipio")
    
    # Extract coefficients and SE's and add them to the dataframe
    coefficients <- coef(wind_total_fe)
    coefficients_df <- rbind(coefficients_df, coefficients)
    se_df <- se(wind_total_fe)
    se_df <- rbind(se_df, se_df)
}

colnames(coefficients_df) <- c(-37,-35:25)
coefficients_df$`-36` <- 0
coefficients_df<-coefficients_df%>%mutate(iteration=seq(1:76))


# Reshape the dataframe into long format
coefficients_df_long <- coefficients_df %>%
  gather(key = "t", value = "coef",-iteration) 

coefficients_df_long$t<-as.numeric(coefficients_df_long$t)

# Plot using ggplot
all_subgroups_wind<-ggplot(coefficients_df_long, aes(x = t, y = coef, group = as.factor(iteration), color = as.factor(iteration))) +
  geom_line() +
  geom_point()+
  labs(x = "Months before/after commissioning", y = "Jobs/MW", title = "b. Wind") +
  theme_bw()+
  theme(legend.position = "none")+scale_x_continuous(breaks=c(-37,seq(-32,20,4),25),labels = c(paste("-37+"),seq(-32,20,4),paste("25+")),expand = c(0.01,0.01))+geom_vline(xintercept = 0, linetype="dashed")+geom_hline(yintercept = 0, linetype="dashed")
```

solar Robustness: Leave-one-out estimation of total employment (always leaving one subgroup out)
```{r}
# Get unique values of subclass_solar
unique_subclass_solar <- unique(solar_matched_final_monthly$subclass_solar)

# Initialize an empty dataframe to store coefficients
coefficients_df <- data.frame()
se_df <- data.frame()
# Loop over unique values of subclass_solar and run regression
for (i in unique_subclass_solar) {
    # Filter out the current value of subclass_solar
    filtered_data <- solar_matched_final_monthly[solar_matched_final_monthly$subclass_solar != i, ]
    
  
    
    # Run the regression
    solar_total_form <- xpd(solar_jobs_endmonth ~ d_solar_pre37_bin+ d_solar_pre.[35:1] + new_mw_solar + d_solar_post.[1:24] + d_solar_post25_bin | id_municipio + month^ano)
    solar_total_fe <- feols(solar_total_form, filtered_data, cluster = "id_municipio")
    
    # Extract coefficients and SE's and add them to the dataframe
    coefficients <- coef(solar_total_fe)
    coefficients_df <- rbind(coefficients_df, coefficients)
    se_df <- se(solar_total_fe)
    se_df <- rbind(se_df, se_df)
}

colnames(coefficients_df) <- c(-37,-35:25)
coefficients_df$`-36` <- 0
coefficients_df<-coefficients_df%>%mutate(iteration=seq(1:31))

# Reshape the dataframe into long format
coefficients_df_long <- coefficients_df %>%
  gather(key = "t", value = "coef",-iteration) 

coefficients_df_long$t<-as.numeric(coefficients_df_long$t)

# Plot using ggplot
all_subgroups_solar<-ggplot(coefficients_df_long, aes(x = t, y = coef, group = as.factor(iteration), color = as.factor(iteration))) +
  geom_line() +
  geom_point()+
  labs(x = "Months before/after commissioning", y = "Jobs/MW", title = "a. Solar") +
  theme_bw()+
  theme(legend.position = "none")+scale_x_continuous(breaks=c(-37,seq(-32,20,4),25),labels = c(paste("-37+"),seq(-32,20,4),paste("25+")),expand = c(0.01,0.01))+geom_vline(xintercept = 0, linetype="dashed")+geom_hline(yintercept = 0, linetype="dashed")
library(patchwork)
joint_plot<-all_subgroups_solar+all_subgroups_wind
ggsave(joint_plot, file=here("output","regressions","TWFE 1-to-1 binning","final figures","appendix", "leave1_out.png"), width=2000, height=1000,units="px")

#The second "peak" is completely gone in iteration 4 where subclass 9 is excluded
no_outliers<-solar_matched_final_monthly%>%filter(subclass_solar!=9)
    solar_total_form <- xpd(solar_jobs_endmonth ~ d_solar_pre37_bin+ d_solar_pre.[35:1] + new_mw_solar + d_solar_post.[1:24] +d_solar_post25_bin | id_municipio + month^ano)
    solar_total_fe <- feols(solar_total_form, no_outliers, cluster = "id_municipio")
    summary(solar_total_fe)
    
subclass9<-solar_matched_final_monthly%>%filter(subclass_solar==9, t_solar>-10)%>%select(id_municipio, new_mw_solar, total_endmonth, solar_jobs_endmonth,solar_treat_postmatch,subclass_solar, t_solar) 
```

wind Robustness: Leave-one-out estimation of GDP
```{r}
# Get unique values of subclass_wind
unique_subclass_wind <- unique(wind_matched_final_annual$subclass_wind)

# Initialize an empty dataframe to store coefficients
coefficients_df <- data.frame()
se_df <- data.frame()
# Loop over unique values of subclass_wind and run regression
for (i in unique_subclass_wind) {
    # Filter out the current value of subclass_wind
    filtered_data <- wind_matched_final_annual[wind_matched_final_annual$subclass_wind != i, ]
    
      # Define the column numbers from -36 to +24
    column_numbers <- c(-7:-1, 1:5)
    
    # Run the regression
    wind_total_form <- xpd(pib_clean_constant2020_BRL ~ d_wind_pre7_bin + d_wind_pre.[6:4]+ d_wind_pre.[2:1] + new_mw_wind + d_wind_post.[1:5]+d_wind_post6_bin | id_municipio + ano)
    wind_total_fe <- feols(wind_total_form, filtered_data, cluster = "id_municipio")
    
    # Extract coefficients and SE's and add them to the dataframe
    coefficients <- coef(wind_total_fe)
    coefficients_df <- rbind(coefficients_df, coefficients)
    se_df <- se(wind_total_fe)
    se_df <- rbind(se_df, se_df)
}

colnames(coefficients_df) <- c(-7:-4,-2:-1, 0, 1:6)
coefficients_df$`-3` <- 0
coefficients_df<-coefficients_df%>%mutate(iteration=seq(1:76))

# Reshape the dataframe into long format
coefficients_df_long <- coefficients_df %>%
  gather(key = "t", value = "coef",-iteration) 

coefficients_df_long$t<-as.numeric(coefficients_df_long$t)

# Plot using ggplot
all_subgroups_wind<-ggplot(coefficients_df_long, aes(x = t, y = coef, group = as.factor(iteration), color = as.factor(iteration))) +
  geom_line() +
  geom_point()+
  labs(x = "Years before/after commissioning", y = "Jobs/MW", title = "b. Wind") +
  theme_bw()+
  theme(legend.position = "none")+scale_x_continuous(breaks=seq(-7,6,1), labels = c(paste("-7+"),seq(-6,5,1),paste("6+")))+
  geom_vline(xintercept = 0, linetype="dashed")+geom_hline(yintercept = 0, linetype="dashed")

```

solar Robustness: Leave-one-out estimation of GDP
```{r}
# Get unique values of subclass_solar
unique_subclass_solar <- unique(solar_matched_final_annual$subclass_solar)

# Initialize an empty dataframe to store coefficients
coefficients_df <- data.frame()
se_df <- data.frame()
# Loop over unique values of subclass_solar and run regression
for (i in unique_subclass_solar) {
    # Filter out the current value of subclass_solar
    filtered_data <- solar_matched_final_annual[solar_matched_final_annual$subclass_solar != i, ]
    
      # Define the column numbers from -36 to +24
    column_numbers <- c(-7:-1, 1:3)
    
    # Run the regression
    solar_total_form <- xpd(pib_clean_constant2020_BRL ~ d_solar_pre7_bin+ d_solar_pre.[6:4]+d_solar_pre.[2:1] + new_mw_solar + d_solar_post.[1:3]+d_solar_post4_bin | id_municipio + ano)
    solar_total_fe <- feols(solar_total_form, filtered_data, cluster = "id_municipio")
    
    # Extract coefficients and SE's and add them to the dataframe
    coefficients <- coef(solar_total_fe)
    coefficients_df <- rbind(coefficients_df, coefficients)
    se_df <- se(solar_total_fe)
    se_df <- rbind(se_df, se_df)
}

colnames(coefficients_df) <- c(-7:-4,-2,-1,0, 1:4)
coefficients_df$`-3` <- 0
coefficients_df<-coefficients_df%>%mutate(iteration=seq(1:31))

# Reshape the dataframe into long format
coefficients_df_long <- coefficients_df %>%
  gather(key = "t", value = "coef",-iteration) 

coefficients_df_long$t<-as.numeric(coefficients_df_long$t)

# Plot using ggplot
all_subgroups_solar<-ggplot(coefficients_df_long, aes(x = t, y = coef, group = as.factor(iteration), color = as.factor(iteration))) +
  geom_line() +
  geom_point()+
  labs(x = "Years before/after commissioning", y = "Jobs/MW", title = "a. Solar") +
  theme_bw()+
  theme(legend.position = "none")+scale_x_continuous(breaks=seq(-7,4,1),labels = c(paste("-7+"),seq(-6,3,1),paste("4+")))+geom_vline(xintercept = 0, linetype="dashed")+geom_hline(yintercept = 0, linetype="dashed")

joint_plot<-all_subgroups_solar+all_subgroups_wind
ggsave(joint_plot, file=here("output","regressions","TWFE 1-to-1 binning","final figures","appendix", "leave1_out_gdp.png"), width=2000, height=1000,units="px")
```

Auction prices
```{r}
auction_file<-fread(here("raw","resultado-leiloes-geracao.csv"), sep = ';', encoding = "Latin-1", dec=",")
ipca<-readRDS(here("raw","ipca_deflator.RDS"))
ipca <- type.convert(ipca, as.is = TRUE)

auction_file<-auction_file%>%left_join(ipca, by=c("AnoLeilao"="ano"))%>%
  mutate(auction_price_2020_BRL=VlrPrecoLeilao*deflator)


mean(auction_file$VlrPrecoLeilao[auction_file$SigTipoGeracao=="EOL" & auction_file$MdaPotenciaInstaladaMW>5])
mean(auction_file$auction_price_2020_BRL[auction_file$SigTipoGeracao=="EOL" & auction_file$MdaPotenciaInstaladaMW>5])

median(auction_file$VlrPrecoLeilao[auction_file$SigTipoGeracao=="EOL"])

hist(auction_file$VlrPrecoLeilao[auction_file$SigTipoGeracao=="EOL" & auction_file$MdaPotenciaInstaladaMW>5])
#How much money do you make per year with the average elecricity tariff from the wind auctions and the average capacity factor and average size?
122.3066*365*24*0.37*51
#=20,217,428
174.1861*365*24*0.37*51
#28,793,171

mean(auction_file$VlrPrecoLeilao[auction_file$SigTipoGeracao=="UFV"& auction_file$MdaPotenciaInstaladaMW>5])
mean(auction_file$auction_price_2020_BRL[auction_file$SigTipoGeracao=="UFV" & auction_file$MdaPotenciaInstaladaMW>5])
median(auction_file$VlrPrecoLeilao[auction_file$SigTipoGeracao=="UFV"])
198.9908*365*24*0.23*61
#24,456,526

236.2345*365*24*0.23*61
#29,033,882
```

total number of firms and employees in Turbine manufacturing
```{r}
turbine_manufacturers<-readRDS(here("final", "turbine_manufacturers.RDS"))
library(patchwork)
a<-ggplot(turbine_manufacturers, aes(ano,total_jobs))+geom_line()+geom_point()+labs(x="Year",y= "No.")+scale_x_continuous(breaks=seq(2006,2021,2))+ggtitle("a. Total number of employees")+theme_bw()

b<-ggplot(turbine_manufacturers, aes(ano,no_establishments))+geom_line()+geom_point()+labs(x="Year", y="No.")+scale_x_continuous(breaks=seq(2006,2021,2))+ggtitle("b. Number of active firms")+theme_bw()

c<-ggplot(turbine_manufacturers, aes(ano,share_jobs))+geom_line()+geom_point()+labs(x="Year",y= "%")+scale_x_continuous(breaks=seq(2006,2021,2))+ggtitle("c. Share of total employees")+theme_bw()

d<-ggplot(turbine_manufacturers, aes(ano,share_of_totalfirms))+geom_line()+geom_point()+labs(x="Year", y="%")+scale_x_continuous(breaks=seq(2006,2021,2))+ggtitle("d. Share of total active firms")+theme_bw()


manuf_plot<-a+b+c+d
ggsave(manuf_plot, file=here("output","regressions","TWFE 1-to-1 binning","final figures","appendix", "turbine_manufacturers.png"), width=2000, height=2000,units="px")

```


