---
title: "2- load administrative data"
author: "Fabian Scheifele"
date: "2023-02-06"
output: html_document
editor_options: 
  chunk_output_type: console
---
0. load packages
```{r setup, include=FALSE}
suppressMessages(memory.limit(size = NA))

if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}
suppressMessages(install_load("tidyverse", "dplyr", "ggplot2", "readr", "readxl","knitr","here", "data.table","basedosdados","bigrquery", "dbplyr","janitor","fuzzyjoin","zoo", "purrr", "stringr"))

`%notin%` <- Negate(`%in%`)
```

1. set the google cloud console ID and project
```{r}
#PLEASE ENTER YOUR OWN BILLING ID from Google Console
set_billing_id("")
```



5. PIB, population and 
```{r}
pib<-basedosdados::read_sql(query="SELECT * FROM `basedosdados.br_ibge_pib.municipio`")
saveRDS(pib,here("raw","pib.RDS"))
population<-basedosdados::read_sql(query="SELECT * FROM `basedosdados.br_ibge_populacao.municipio`
    WHERE ano BETWEEN 2000 AND 2022")
saveRDS(population,here("raw","population.RDS") )
```

6. SICONFI
```{r}
siconfi_spending <- basedosdados::read_sql(query = "SELECT ano, id_municipio, id_conta_bd, valor FROM `basedosdados.br_me_siconfi.municipio_despesas_funcao`
  WHERE ano BETWEEN 2000 AND 2023
    AND estagio_bd = 'Despesas Empenhadas'
    AND id_conta_bd IN (
      '3.00.000',
      '3.08.000',
      '3.09.000',
      '3.10.000',
      '3.11.000',
      '3.12.000',
      '3.15.000',
      '3.16.000',
      '3.17.000',
      '3.18.000',
      '3.19.000',
      '3.20.000',
      '3.21.000',
      '3.22.000',
      '3.23.000',
      '3.25.000',
      '3.26.000'
    )
")


siconfi_spending<-siconfi_spending%>%separate(id_conta_bd, c("group", "subgroup", "subsubgroup"),remove = FALSE)
saveRDS(siconfi_spending, here("raw","siconfi_spending.RDS"))

siconfi_receipts<-basedosdados::read_sql(query=
  "SELECT ano, id_municipio, estagio_bd, portaria, conta_bd, valor
    FROM `basedosdados.br_me_siconfi.municipio_receitas_orcamentarias`
   where ano between 2000 and 2023")
saveRDS(siconfi_receipts,here("raw","siconfi_receipts.RDS") )


categories<-basedosdados::read_sql(query="SELECT DISTINCT id_conta_bd, conta_bd, 
      FROM `basedosdados.br_me_siconfi.municipio_despesas_funcao`")

saveRDS(categories, here("raw","siconfi_spending_cats.RDS"))

categories2<-basedosdados::read_sql(query="SELECT DISTINCT id_conta_bd, conta_bd, 
      FROM `basedosdados.br_me_siconfi.municipio_receitas_orcamentarias`")

saveRDS(categories2, here("raw","siconfi_receipt_cats.RDS"))
```

7. Broadband access
```{r}
#take broadband access at the end of the year as additional variable
broadband<-basedosdados::read_sql(query=
  "SELECT ano, id_municipio, acessos, densidade 
  FROM `basedosdados.br_anatel_banda_larga_fixa.densidade_municipio` 
  WHERE mes=12")
#remove duplicates
broadband_distinct<-broadband%>%distinct(ano, id_municipio, .keep_all = TRUE)
saveRDS(broadband_distinct,here("raw","broadband_access.RDS"))
```

8. Municipal Development Index
```{r}
idfm_general<-read_excel(here("raw","IFDM Geral_2005 a 2016.xlsx"), col_names = FALSE)
idfm_general <- idfm_general[-c(1,2),]
idfm_general<-idfm_general %>%row_to_names(row_number = 1)%>%
  clean_names()

idfm_general<-idfm_general%>%
  rename("2005"=nota)%>%
  rename("2006"=nota_2)%>%
  rename("2007"=nota_3)%>%
  rename("2008"=nota_4)%>%
   rename("2009"=nota_5)%>%
   rename("2010"=nota_6)%>%
   rename("2011"=nota_7)%>%
   rename("2012"=nota_8)%>%
   rename("2013"=nota_9)%>%
   rename("2014"=nota_10)%>%
   rename("2015"=nota_11)%>%
   rename("2016"=nota_12)

idfm_general<-idfm_general%>%
  select(-starts_with("ranking"),-municipio,-regiao,-uf)

idfm_long<-idfm_general %>% 
  pivot_longer(
    cols = `2005`:`2016`, 
    names_to = "year",
    values_to = "munic_index_general"
)

idfm_renda<-read_excel(here("raw","IFDM EmpregoRenda-2005-2016.xlsx"), col_names = FALSE)
idfm_renda <- idfm_renda[-c(1,2),]
idfm_renda<-idfm_renda %>%row_to_names(row_number = 1)%>%
  clean_names()

idfm_renda<-idfm_renda%>%
  rename("2005"=nota)%>%
  rename("2006"=nota_2)%>%
  rename("2007"=nota_3)%>%
  rename("2008"=nota_4)%>%
   rename("2009"=nota_5)%>%
   rename("2010"=nota_6)%>%
   rename("2011"=nota_7)%>%
   rename("2012"=nota_8)%>%
   rename("2013"=nota_9)%>%
   rename("2014"=nota_10)%>%
   rename("2015"=nota_11)%>%
   rename("2016"=nota_12)

idfm_renda<-idfm_renda%>%
  select(-starts_with("ranking"),-municipio,-regiao,-uf)

idfm_renda_long<-idfm_renda %>% 
  pivot_longer(
    cols = `2005`:`2016`, 
    names_to = "year",
    values_to = "munic_index_renda"
)

idfm_long<-idfm_long%>%left_join(idfm_renda_long, by=c("codigo","year"))

#2018 data
idfm_2018<-read_excel(here("raw","IFDM 2018.xlsx"), col_names = FALSE)
idfm_2018 <- idfm_2018[-c(1:6,8),]
idfm_2018<-idfm_2018 %>%row_to_names(row_number = 1)%>%
  clean_names()
idfm_2018<-idfm_2018%>%
  rename(codigo=na_2)%>%
  rename(munic_index_general=ifdm)%>%
  rename(munic_index_renda=emprego_renda)%>%
  mutate(year=2018)
idfm_2018<-idfm_2018%>%
  select(codigo,year,munic_index_general,munic_index_renda)
idfm_2018$codigo<-as.character(idfm_2018$codigo)
idfm_2018$year<-as.character(idfm_2018$year)
idfm_long<-bind_rows(idfm_long,idfm_2018)

saveRDS(idfm_long, here("intermediate","municipal_index.RDS"))
```

9. Electricity Outages Data (ANEEL, 2017-2022)
```{r}
#Load the linking table
municipalities<-fread(here("raw","indqual-municipio.csv"), encoding="Latin-1")%>%
  select(2,3)

#Restrict analysis to non-programmed outages and calculate average 
outages_2017<-fread(here("raw","interrupcoes-energia-eletrica-2017.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))

outages_2017<-outages_2017%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#consumer unit often relates to multiple municipalities,however since the municipality is fully affected I will not do fractional counts but count the outage as 1 for each municipality

#Summarise number and average duration of outage by municipality ID 
outages_2017_agg<-outages_2017%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))

remove(outages_2017)

outages_2018<-fread(here("raw","interrupcoes-energia-eletrica-2018.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#Summarise number and average duration of outage by area (abadia dos dorados had 1244)
outages_2018_agg<-outages_2018%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))
remove(outages_2018)

outages_2019<-fread(here("raw","interrupcoes-energia-eletrica-2019.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#Summarise number and average duration of outage by area (abadia dos dorados had 1244)
outages_2019_agg<-outages_2019%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))
remove(outages_2019)

outages_2020<-fread(here("raw","interrupcoes-energia-eletrica-2020.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#Summarise number and average duration of outage by area (abadia dos dorados had 1244)
outages_2020_agg<-outages_2020%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))
remove(outages_2020)

outages_2021<-fread(here("raw","interrupcoes-energia-eletrica-2021.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#Summarise number and average duration of outage by area (abadia dos dorados had 1244)
outages_2021_agg<-outages_2021%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))
remove(outages_2021)

outages_2022<-fread(here("raw","interrupcoes-energia-eletrica-2022.csv"), encoding = "Latin-1")%>%
  filter(TipoInt=="Não Programada")%>%
  mutate(time_interruption=(DtFimInt-DtInicioInt))%>%
  left_join(municipalities, by=c("IdeCnjUndCnm"="IdeConjUnidConsumidoras"))

#Summarise number and average duration of outage by area (abadia dos dorados had 1244)
outages_2022_agg<-outages_2022%>%
  group_by(CodMunicipio, Ano)%>%
  summarise(unprogrammed_outages=n(), avg_time=mean(time_interruption))
remove(outages_2022)

#bind together
Names <- ls(pattern = "^outages_")
L <- mget(Names)
outages_final<-bind_rows(L)
outages_final<-outages_final%>%mutate(avg_interruption_in_hours=avg_time/3600)
outages_final$avg_interruption_in_hours<-as.numeric(outages_final$avg_interruption_in_hours)
outages_final<-outages_final%>%select(-avg_time)

saveRDS(outages_final,here("intermediate","outages_2017_2022.RDS"))
rm(list = ls())
```



14. geographic data
```{r}
municipality_names<-basedosdados::read_sql(query="SELECT DISTINCT id_municipio, nome_municipio FROM `basedosdados.br_geobr_mapas.setor_censitario_2010`")
geobr<-basedosdados::read_sql(query="SELECT * FROM `basedosdados.br_geobr_mapas.municipio`")
municipalities<-full_join(municipality_names,geobr, by="id_municipio")

saveRDS(municipalities, here("raw","geodata_municipios.RDS"))
```

15.load firm-level of operators (Sviatlana)
```{r}
#load auction generation file to extract cpnj number
auction_generation_final <-
  readRDS(here("final", "auction_generation_final.RDS"))

# extract CNPJs as a vector
cnpjs <- auction_generation_final$NumCPFCNPJ

# convert vector to a string of comma-separated values
cnpjs_str <-
  paste0("'", gsub("'", "\\'", cnpjs), "'", collapse = ",")
# extract establishments from database
estabelecimentos <-
  basedosdados::read_sql(
    query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, data_inicio_atividade, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral
                              FROM `basedosdados.br_me_cnpj.estabelecimentos`
                              WHERE cnpj IN(",
      cnpjs_str,
      ")  AND data = '2022-12-17'"
    )
  )

# extract CNPJs basico as a vector
cnpj_basic <- estabelecimentos$cnpj_basico
# convert vector to a string of comma-separated values
cnpj_basico_str <-
  paste0("'", gsub("'", "\\'", cnpj_basic), "'", collapse = ",")

#get all establishments connected with enterprises by CNPJs basico
estabelecimentos_all <-
  basedosdados::read_sql(
    query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, data_inicio_atividade, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral
                              FROM `basedosdados.br_me_cnpj.estabelecimentos`
                              WHERE cnpj_basico IN(",
      cnpj_basico_str,
      ")  AND data = '2022-12-17'"
    )
  )


estabelecimentos_all$Basico <- ifelse(estabelecimentos_all$cnpj_basico %in% cnpj_basic, 1, 0)

#get enterprise from the database
socios <-
  basedosdados::read_sql(
    query = paste(
      "SELECT nome, cnpj_basico, tipo, id_pais
                            FROM `basedosdados.br_me_cnpj.socios`
                              WHERE cnpj_basico IN(",
      cnpj_basico_str,
      ")  AND data = '2022-12-17'"
    )
  )



#flag to check if the company is foreign or not. 105 - code of brasil from siscomex_country_code
socios <- socios %>% mutate(notBrasil = NA)

for (i in 1:nrow(socios)) {
  if (is.na(socios$id_pais[i]) || socios$id_pais[i] == 105) {
    socios$notBrasil[i] = FALSE
  }
  else
    socios$notBrasil[i] = TRUE
}


#reduce the owner data to whether company is partially foreign-owned or not
socios <- socios %>%
  group_by(cnpj_basico) %>%
  mutate(foreign = any(notBrasil == TRUE)) %>%
  ungroup()

socios_final<-socios%>%distinct(cnpj_basico, foreign)

# left join establishment and company data by cnpj_basico
estabelecimentos_all1 <-
  estabelecimentos_all %>% left_join(socios_final, by = c("cnpj_basico" = "cnpj_basico"))

#determine if the establishment is our operator
estabelecimentos_all1 <- estabelecimentos_all1 %>% mutate(operator = NA)

estabelecimentos_all1$operator <-
  ifelse(estabelecimentos_all1$cnpj %in% estabelecimentos$cnpj, 1, 0)

#keep only operators and mother companies
estabelecimentos_all2<-estabelecimentos_all1%>%filter(identificador_matriz_filial==1 | operator==1)%>%
  select(cnpj,cnpj_basico,identificador_matriz_filial,cnae_fiscal_principal,id_municipio,foreign,operator)

#make it wide format (1 row=1 company)
mother_companies<-estabelecimentos_all2%>%filter(identificador_matriz_filial==1)%>%
  select(cnpj_basico,cnae_fiscal_principal,id_municipio)%>%
  rename(cnae_mother_company=cnae_fiscal_principal, mun_id_mother=id_municipio)

#reduce to 1 row per company, keeping only foreign plus CNAE and municipality of operator and of mother company
estabelecimentos_final <-
  estabelecimentos_all1 %>%filter(operator==1)%>%select(cnpj, cnpj_basico, id_municipio, cnae_fiscal_principal, foreign, identificador_matriz_filial) %>%
  left_join(mother_companies, by=c("cnpj_basico"))

saveRDS(estabelecimentos_final,
        here("intermediate", "estabelecimentos.RDS"))

```

16. load firm-level info of wind manufacturer
```{r}
wind_manufacturer<-read_excel(here("raw", "CNPJs.xlsx"), sheet = "wind")

#remove companies, which are not wind manufactures from the dataset
wind_manufacturer <- subset(wind_manufacturer, !is.na(wind_manufacturer[, 5]) | !is.na(wind_manufacturer[, 6]) | !is.na(wind_manufacturer[, 7])) 
wind_manufacturer <- wind_manufacturer%>%select(1:7)

# filter NA CNPJs
wind_manufacturer <- wind_manufacturer %>% 
  filter(!is.na(CNPJ))

#Bring CNPJs to the correct format to use it for the SQL query
wind_manufacturer <- wind_manufacturer %>%
  mutate(CNPJ = gsub("[\\./\\-]","", `CNPJ format`))


# extract CNPJs as a vector
cnpjs_wind <- wind_manufacturer$CNPJ
# convert vector to a string of comma-separated values
cnpjs_str_wind <-paste0("'", gsub("'", "\\'", cnpjs_wind), "'", collapse = ",")

# extract establishments_wind from database
estabelecimentos_wind <-basedosdados::read_sql( query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral, nome_fantasia
      FROM `basedosdados.br_me_cnpj.estabelecimentos`
      WHERE cnpj IN(",cnpjs_str_wind, ")  AND data = '2022-12-17'"
    )
  )

# extract CNPJs basico as a vector
cnpj_basic_wind <- estabelecimentos_wind$cnpj_basico
# convert vector to a string of comma-separated values
cnpj_basico_str_wind <-paste0("'", gsub("'", "\\'", cnpj_basic_wind), "'", collapse = ",")

#get all establishments connected with enterprises by CNPJs basico
estabelecimentos_all_wind <-
  basedosdados::read_sql(
    query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral, nome_fantasia
                              FROM `basedosdados.br_me_cnpj.estabelecimentos`
                              WHERE cnpj_basico IN(", cnpj_basico_str_wind, ")  AND data = '2022-12-17'"
    )
  )


#get enterprise from the database
socios_wind <-
  basedosdados::read_sql(
    query = paste(
      "SELECT nome, cnpj_basico, tipo, id_pais
                            FROM `basedosdados.br_me_cnpj.socios`
                              WHERE cnpj_basico IN(",
      cnpj_basico_str_wind,
      ")  AND data = '2022-12-17'"
    )
  )



#flag to check if the company is foreign or not. 105 - code of brasil from siscomex_country_code
socios_wind <- socios_wind %>% mutate(notBrasil = NA)

for (i in 1:nrow(socios_wind)) {
  if (is.na(socios_wind$id_pais[i]) || socios_wind$id_pais[i] == 105) {
    socios_wind$notBrasil[i] = FALSE
  }
  else
    socios_wind$notBrasil[i] = TRUE
}


#reduce the owner data to whether company is partially foreign-owned or not
socios_wind <- socios_wind %>%
  group_by(cnpj_basico) %>%
  mutate(foreign = any(notBrasil == TRUE)) %>%
  ungroup()

socios_final_wind<-socios_wind%>%distinct(cnpj_basico, foreign)

# left join establishment and company data by cnpj_basico
estabelecimentos_final_wind <-
  estabelecimentos_all_wind %>% left_join(socios_final_wind, by = c("cnpj_basico" = "cnpj_basico"))

estabelecimentos_final_wind <- estabelecimentos_final_wind %>% 
  rename(
    activity_start = data_inicio_atividade,
    registration_status = situacao_cadastral, 
    end_date = data_situacao_cadastral
    )

estabelecimentos_final_wind <- subset(estabelecimentos_final_wind, estabelecimentos_final_wind$registration_status != 1)

for (i in 1:nrow(estabelecimentos_final_wind)) {
  if(estabelecimentos_final_wind$registration_status[i] == 2){
    estabelecimentos_final_wind$end_date[i]<- NA
  }
 } 



estabelecimentos_final_wind <- estabelecimentos_final_wind %>%
  mutate(start_year = year(activity_start),
         start_month = month(activity_start)) %>%
  mutate(end_year = year(end_date),
         end_month = month(end_date))

saveRDS(estabelecimentos_final_wind,
        here("intermediate", "estabelecimentos_wind.RDS"))


estabelecimentos_matriz_cnae_d<- estabelecimentos_final_wind %>% filter(identificador_matriz_filial == 1) %>% distinct(cnae_fiscal_principal)

estabelecimentos_final_wind$manufacturer <- ifelse(estabelecimentos_final_wind$cnpj %in% cnpjs_wind, TRUE, FALSE)


```

17. load firm-level info of solar manufacturer 
```{r}
solar_manufacturer<-read_excel(here("raw", "CNPJs.xlsx"), sheet ="solar")
solar_manufacturer <- solar_manufacturer%>%select(1:10)


#Bring CNPJs to the correct format to use it for the SQL query
solar_manufacturer <- solar_manufacturer %>%
  mutate(CNPJ = gsub("[\\./\\-]","", `CNPJ format`))

solar_manufacturer <- solar_manufacturer %>% 
  filter(!is.na(CNPJ))

# extract CNPJs as a vector
cnpjs_solar <- solar_manufacturer$CNPJ

# convert vector to a string of comma-separated values
cnpjs_str_solar <-
  paste0("'", gsub("'", "\\'", cnpjs_solar), "'", collapse = ",")


#extracting data for the solar manufacturers

# extract establishments_solar from database
estabelecimentos_solar <-
  basedosdados::read_sql(
    query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral, nome_fantasia
                              FROM `basedosdados.br_me_cnpj.estabelecimentos`
                              WHERE cnpj IN(",
      cnpjs_str_solar,
      ")  AND data = '2022-12-17'"
    )
  )

# extract CNPJs basico as a vector
cnpj_basico_solar <- estabelecimentos_solar$cnpj_basico

# convert vector to a string of comma-separated values
cnpj_basico_str_solar <-
  paste0("'", gsub("'", "\\'", cnpj_basico_solar), "'", collapse = ",")

#get all establishments connected with enterprises by CNPJs basico
estabelecimentos_all_solar <-
  basedosdados::read_sql(
    query = paste(
      "SELECT cnpj, cnpj_basico, identificador_matriz_filial, id_pais, data_inicio_atividade, cnae_fiscal_principal, id_municipio, data, situacao_cadastral, data_situacao_cadastral, motivo_situacao_cadastral, nome_fantasia
                              FROM `basedosdados.br_me_cnpj.estabelecimentos`
                              WHERE cnpj_basico IN(",
      cnpj_basico_str_solar,
      ")  AND data = '2022-12-17'"
    )
  )


#get enterprise from the database
socios_solar <-
  basedosdados::read_sql(
    query = paste(
      "SELECT nome, cnpj_basico, tipo, id_pais
                            FROM `basedosdados.br_me_cnpj.socios`
                              WHERE cnpj_basico IN(",
      cnpj_basico_str_solar,
      ")  AND data = '2022-12-17'"
    )
  )



#flag to check if the company is foreign or not. 105 - code of brasil from siscomex_country_code
socios_solar <- socios_solar %>% mutate(notBrasil = NA)

for (i in 1:nrow(socios_solar)) {
  if (is.na(socios_solar$id_pais[i]) || socios_solar$id_pais[i] == 105) {
    socios_solar$notBrasil[i] = FALSE
  }
  else
    socios_solar$notBrasil[i] = TRUE
}


#reduce the owner data to whether company is partially foreign-owned or not
socios_solar <- socios_solar %>%
  group_by(cnpj_basico) %>%
  mutate(foreign = any(notBrasil == TRUE)) %>%
  ungroup()

socios_final_solar<-socios_solar%>%distinct(cnpj_basico, foreign)

# left join establishment and company data by cnpj_basico
estabelecimentos_all_solar <-
  estabelecimentos_all_solar %>% left_join(socios_final_solar, by = c("cnpj_basico" = "cnpj_basico"))


estabelecimentos_final_solar <- estabelecimentos_all_solar %>% 
  rename(
    activity_start = data_inicio_atividade,
    registration_status = situacao_cadastral, 
    end_date = data_situacao_cadastral
    )

estabelecimentos_final_solar <- subset(estabelecimentos_final_solar, estabelecimentos_final_solar$registration_status != 1)

for (i in 1:nrow(estabelecimentos_final_solar)) {
  if(estabelecimentos_final_solar$registration_status[i] == 2){
    estabelecimentos_final_solar$end_date[i]<- NA
  }
 } 


estabelecimentos_final_solar <- estabelecimentos_final_solar %>%
  mutate(start_year = year(activity_start),
         start_month = month(activity_start)) %>%
  mutate(end_year = year(end_date),
         end_month = month(end_date))


# check if establishment is in the initial manufacturer list
estabelecimentos_final_solar$manufacturer <- ifelse(estabelecimentos_final_solar$cnpj %in% cnpjs_solar, TRUE, FALSE)

estabelecimentos_matriz_cnae_distinct<- estabelecimentos_final_solar %>% filter(identificador_matriz_filial == 1) %>% distinct(cnae_fiscal_principal)

saveRDS(estabelecimentos_final_solar,
        here("intermediate", "estabelecimentos_solar.RDS"))

```

18. IPCA deflator
```{r}
ipca<-read_sql("SELECT ano, mes, indice, variacao_anual, variacao_doze_meses FROM `basedosdados.br_ibge_ipca.mes_brasil`")
ipca<-ipca%>%arrange(ano,mes)
ipca<-ipca%>%filter(mes==12)%>%select(1:3)%>%mutate(deflator93=indice/100)%>%select(1,4)
ipca<-ipca%>%mutate(deflator=deflator93[ano==2020]/deflator93)
ipca<-ipca%>%select(ano,deflator)
saveRDS(ipca, here("raw","ipca_deflator.RDS"))

#create monthly deflator
ipca_monthly<-read_sql("SELECT ano, mes, indice, variacao_anual, variacao_doze_meses FROM `basedosdados.br_ibge_ipca.mes_brasil`")
ipca_monthly<-ipca_monthly%>%arrange(ano,mes)
ipca_monthly<-ipca_monthly%>%mutate(deflator93=indice/100)%>%
  mutate(deflator122020=deflator93[ano==2020 & mes==12]/deflator93)
ipca_monthly<-ipca_monthly%>%select(ano,mes,deflator122020)
ipca_monthly <- type.convert(ipca_monthly, as.is = TRUE) 
saveRDS(ipca_monthly, here("raw","ipca_deflator_monthly.RDS"))
```

19. Create registry of newly created firms (all firms 581 Mio. rows! so need to restrict)
```{r}
all_firms<-basedosdados::read_sql(query="SELECT EXTRACT(year FROM data_inicio_atividade) AS year,
      EXTRACT(month FROM data_inicio_atividade) AS month,
      id_municipio,cnae_fiscal_principal, 
      COUNT(*) AS establishments_founded, 
      COUNT(CASE WHEN identificador_matriz_filial = '1' THEN 1 END) AS mother_companies_founded,
      COUNT(CASE WHEN id_pais IS NOT NULL AND id_pais !='105' THEN 1 END) AS foreign_owned_establishment
FROM basedosdados.br_me_cnpj.estabelecimentos
WHERE data_inicio_atividade >= '2005-01-01' and data ='2022-11-24'
GROUP BY year, month, id_municipio, cnae_fiscal_principal")

saveRDS(all_firms, here("raw","cnpj_cnae_month_year_2005_2022.RDS"))

all_firms<-all_firms%>%arrange(id_municipio, year,month)
month_year<-all_firms%>%distinct(month,year)
```

20. load receipts data for solar/wind municipalities with large treatment effects
```{r}
#Load Data
solar_mun <- readRDS(here("raw", "solar_mun.RDS"))
wind_mun <- readRDS(here("raw", "wind_mun.RDS"))
categories <- read_excel(here("raw", "categories.xlsx"))

# extract municipalities as a vector to use in SQL query 
solar_mun_id <- solar_mun$id_municipio

# extract municipalities as a vector
wind_mun_id <- wind_mun$id_municipio

# convert vector to a string of comma-separated values
solar_mun_id_str <-
  paste0("'", gsub("'", "\\'", solar_mun_id), "'", collapse = ",")

wind_mun_id_str <-
  paste0("'", gsub("'", "\\'", wind_mun_id), "'", collapse = ",")

#Step 1 get raw data for the municipios and years indicated in solar_muns.RDS and wind_muns.RDS
 #siconfi_receipts<-basedosdados::read_sql(query=
# "SELECT ano, id_municipio, portaria, conta, id_conta_bd, conta_bd, valor
 #FROM `basedosdados.br_me_siconfi.municipio_receitas_orcamentarias` WHERE id_municipio IN(", solar_mun_id_str ,") AND ano BETWEEN 2000 AND 2020")

#Step 1 get raw data for the municipios and years indicated in solar_muns.RDS and wind_muns.RDS
query_wind <- paste("SELECT ano, id_municipio, portaria, conta, id_conta_bd, conta_bd, valor FROM `basedosdados.br_me_siconfi.municipio_receitas_orcamentarias` WHERE id_municipio IN(", wind_mun_id_str ,") AND ano BETWEEN 2000 AND 2020")
siconfi_receipts_w <- basedosdados::read_sql(query_wind)

query_solar <- paste0("SELECT ano, id_municipio, portaria, conta, id_conta_bd, conta_bd, valor FROM `basedosdados.br_me_siconfi.municipio_receitas_orcamentarias` WHERE id_municipio IN(", solar_mun_id_str ,") AND ano BETWEEN 2000 AND 2020")
siconfi_receipts_s <- basedosdados::read_sql(query_solar)

saveRDS(siconfi_receipts_w,here("raw","receipts_wind.RDS"))
saveRDS(siconfi_receipts_s,here("raw","receipts_solar.RDS"))

```
