---
title: "3-merge data"
author: "Fabian Scheifele"
date: "2023-02-10"
output: html_document
objective: Merge the different administrative data into a panel dataset on municipality-year level
editor_options: 
  chunk_output_type: console
---
0.load packages
```{r setup, include=FALSE}
suppressMessages(memory.limit(size = NA))

if(!require(install.load)){
  install.packages("install.load")
  library(install.load)
}
suppressMessages(install_load("tidyverse", "dplyr", "ggplot2", "readr", "readxl","knitr","here", "data.table","basedosdados","bigrquery", "dbplyr","janitor","fuzzyjoin","tidyr","stringr", "writexl"))

`%notin%` <- Negate(`%in%`)
basedosdados::set_billing_id("")

```

1. import data that is directly mergable (already on municipal-year level)
```{r}
population<-readRDS(here("raw","population.RDS"))
rais_establishment<-readRDS(here("raw","rais_establishment_alljobs.RDS"))
rais_links<-readRDS(here("intermediate","rais_annual_total2.RDS"))
broadband<-readRDS(here("raw","broadband_access.RDS"))
municipal_index<-readRDS(here("intermediate","municipal_index.RDS"))
population <- type.convert(population, as.is = TRUE)
rais_establishment <- type.convert(rais_establishment, as.is = TRUE)
rais_links <- type.convert(rais_links, as.is = TRUE)
broadband <- type.convert(broadband, as.is = TRUE)
municipal_index <- type.convert(municipal_index, as.is = TRUE)
```

2.merge data that is already at municipality_id-year level
```{r}
#Data cleaning: wherever population=0, turn into NA
population$populacao[population$populacao==0]<-NA
panel<-left_join(population,rais_links,by=c("ano","id_municipio"))

panel<-panel%>%left_join(broadband, by=c("ano","id_municipio"))


#add 6-digit municipality ID (without 7th verification digit)via table from https://groups.google.com/g/qgisbrasil/c/0sEGnF5JGFk

digits<-read_excel(here("raw","GEOCodigo.xls"))%>%select(1:3)%>%
  rename(municipality_name=MUNICÍPIO)
names(digits) <- tolower(names(digits))
digits$ibge_7d<-as.integer(digits$ibge_7d)
digits$ibge_6d<-as.integer(digits$ibge_6d)

panel<-panel%>%left_join(digits, by=c("id_municipio"="ibge_7d"))

#merge municipality index with 6-digit ID
municipal_index$codigo<-as.integer(municipal_index$codigo)
panel<-panel%>%left_join(municipal_index, by=c("ano"="year", "ibge_6d"="codigo"))

#6 municipalities are somehow not in this geocodigo dataset
missing_name<-panel%>%filter(is.na(ibge_6d))%>%distinct(id_municipio,municipality_name,ibge_6d)

rm(list=setdiff(ls(), "panel"))

#adapt variable classes to R-friendly classes
panel <- type.convert(panel, as.is = TRUE) 
panel$munic_index_general<-as.numeric(panel$munic_index_general)
panel$munic_index_renda<-as.numeric(panel$munic_index_renda)
```

2. Deflate wage data and join
```{r}
median_wages<-readRDS(here("raw","median_wages.RDS"))
avg_wages<-readRDS(here("raw","avg_wages.RDS"))
median_wages <- type.convert(median_wages, as.is = TRUE)
avg_wages <- type.convert(avg_wages, as.is = TRUE)
ipca<-readRDS(here("raw","ipca_deflator.RDS"))
ipca <- type.convert(ipca, as.is = TRUE)
avg_wages<-avg_wages%>%left_join(ipca, by=c("ano"))%>%
  mutate(avg_wage_2020_BRL=avg_wage*deflator)
avg_wages<-avg_wages%>%select(1,2,5)
median_wages<-median_wages%>%left_join(ipca, by=c("ano"))%>%
  mutate(median_wage_2020_BRL=median_wage*deflator)%>%select(1,2,5)
panel<-panel%>%left_join(avg_wages, by=c("ano","id_municipio"))
panel<-panel%>%left_join(median_wages, by=c("ano","id_municipio"))

rm(list=setdiff(ls(), "panel"))
```



3. Reduce RAIS establishment level data and merge
```{r}
establishments<-readRDS(here("raw","rais_establishment_alljobs.RDS"))
#convert from integer64 to integer
establishments <- type.convert(establishments, as.is = TRUE) 

#recode firm size buckets for years 2000 and 2001 
establishments$tamanho_estabelecimento<-as.numeric(establishments$tamanho_estabelecimento)
establishments <- establishments%>%group_by(id_municipio,ano)%>%
  mutate(firm_size=tamanho_estabelecimento)%>%
  mutate(firm_size = replace(firm_size, ano == 2000, firm_size+1))%>%
  mutate(firm_size = replace(firm_size, ano == 2001, firm_size+1))

#remove old, dual-coded firm size variable (tamanho_estabelecimento)
establishments<-establishments%>%select(-tamanho_estabelecimento)

#create aggregated data (municipality-year)
establishments_agg<-establishments%>%group_by(id_municipio, ano)%>%
  summarize(total_establishment=sum(no_establishments, na.rm = TRUE),
            total_jobs3112_estab=sum(total_jobs,na.rm = TRUE),
             full_time_jobs_3112=sum(full_time, na.rm = TRUE),
             public_servants_3112=sum(public_jobs, na.rm = TRUE), 
            inactive_establishments=sum(inactive_establishments, na.rm = TRUE))

#need to exclude the inactive establishment from the small firms, otherwise artifically inflated
small_firms<-establishments%>%filter(firm_size<=3)%>%
  group_by(id_municipio, ano)%>%
  summarize(establishments_less10=sum(no_establishments, na.rm = TRUE)-sum(inactive_establishments, na.rm = TRUE))

medium_firms<-establishments%>%filter(firm_size %in%c(4:5))%>%
  group_by(id_municipio, ano)%>%
  summarize(establishments_10_49=sum(no_establishments, na.rm = TRUE))

larger_firms<-establishments%>%filter(firm_size >=6)%>%
  group_by(id_municipio, ano)%>%
  summarize(establishments_above50=sum(no_establishments, na.rm = TRUE))

establishments_agg<-establishments_agg%>%
  left_join(small_firms, by=c("id_municipio","ano"))%>%
   left_join(medium_firms, by=c("id_municipio","ano"))%>%
   left_join(larger_firms, by=c("id_municipio","ano"))

#join with panel
panel<-panel%>%left_join(establishments_agg, by=c("id_municipio","ano"))
rm(list=setdiff(ls(), "panel"))

#private firms
private_firms<-readRDS(here("raw","rais_establishment_private.RDS"))
#convert from integer64 to integer
private_firms <- type.convert(private_firms, as.is = TRUE) 

#recode firm size buckets for years 2000 and 2001 
private_firms$tamanho_estabelecimento<-as.numeric(private_firms$tamanho_estabelecimento)
private_firms <- private_firms%>%group_by(id_municipio,ano)%>%
  mutate(firm_size=tamanho_estabelecimento)%>%
  mutate(firm_size = replace(firm_size, ano == 2000, firm_size+1))%>%
  mutate(firm_size = replace(firm_size, ano == 2001, firm_size+1))

#remove old, dual-coded firm size variable (tamanho_estabelecimento)
private_firms<-private_firms%>%select(-tamanho_estabelecimento)

#create aggregated data (municipality-year)
private_firms_agg<-private_firms%>%group_by(id_municipio, ano)%>%
  summarize(private_est_total=sum(no_establ_private, na.rm = TRUE),
            private_est_inactive=sum(inactive_firms_private,na.rm = TRUE))

small_firms<-private_firms%>%filter(firm_size<=3)%>%
  group_by(id_municipio, ano)%>%
  summarize(private_firms_less10=sum(no_establ_private, na.rm = TRUE)-sum(inactive_firms_private,na.rm = TRUE))

medium_firms<-private_firms%>%filter(firm_size %in%c(4:5))%>%
  group_by(id_municipio, ano)%>%
  summarize(private_firms_10_49=sum(no_establ_private, na.rm = TRUE))

larger_firms<-private_firms%>%filter(firm_size >=6)%>%
  group_by(id_municipio, ano)%>%
  summarize(private_firms_above50=sum(no_establ_private, na.rm = TRUE))

private_firms_agg<-private_firms_agg%>%
  left_join(small_firms, by=c("id_municipio","ano"))%>%
   left_join(medium_firms, by=c("id_municipio","ano"))%>%
   left_join(larger_firms, by=c("id_municipio","ano"))

#join with panel
panel<-panel%>%left_join(private_firms_agg, by=c("id_municipio","ano"))
rm(list=setdiff(ls(), "panel"))
```

4. merge power-related RAIS data
```{r}
cnae_annual<-readRDS(here("intermediate","rais_cnae_annual.RDS"))
panel<-panel%>%left_join(cnae_annual, by=c("ano","id_municipio"))
names<-colnames(panel[33:56])

#replace post 2005 NAs that were created through left join by zeros
panel[panel$ano > 2005, names(panel)] <- lapply(panel[panel$ano > 2005, names(panel)], function(x) ifelse(is.na(x), 0, x))
remove(cnae_annual)
remove(names)
```

5. Merge SICONFI Spending data
```{r}
siconfi_spending<-readRDS(here("raw","siconfi_spending.RDS"))

#adapt class for merge
siconfi_spending <- type.convert(siconfi_spending, as.is = TRUE) 

#aggregate at different level#
#infrastructure (transport 26, urbanism 15, sanitation 17, telecommunication 24)
#environment (18)
#energy (25)
#industry and commerce (22)

siconfi_agg<-siconfi_spending%>%filter(subgroup=="0")%>%
  group_by(id_municipio, ano)%>%
  summarise(total_spending=sum(valor,na.rm=TRUE))

infra<-siconfi_spending%>%filter(subgroup %in% c("26","15","17","24","25"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_infra=sum(valor,na.rm=TRUE))

energy<-siconfi_spending%>%filter(subgroup=="25")%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_energy=sum(valor,na.rm=TRUE))

environ<-siconfi_spending%>%filter(subgroup=="18")%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_environ=sum(valor,na.rm=TRUE))

industry_commerce<-siconfi_spending%>%filter(subgroup %in% c("22","23"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_industry_commerce=sum(valor,na.rm=TRUE))

housing<-siconfi_spending%>%filter(subgroup %in% c("16"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_housing=sum(valor,na.rm=TRUE))

social_assistance<-siconfi_spending%>%filter(subgroup %in% c("8"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_social_ass=sum(valor,na.rm=TRUE))

social_security<-siconfi_spending%>%filter(subgroup %in% c("9"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_social_sec=sum(valor,na.rm=TRUE))

health<-siconfi_spending%>%filter(subgroup %in% c("10"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_health=sum(valor,na.rm=TRUE))

labor<-siconfi_spending%>%filter(subgroup %in% c("11"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_labor=sum(valor,na.rm=TRUE))

education<-siconfi_spending%>%filter(subgroup %in% c("12"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_education=sum(valor,na.rm=TRUE))
 
agriculture<-siconfi_spending%>%filter(subgroup %in% c("20","21"))%>%
  group_by(id_municipio, ano)%>%
  summarise(spending_agriculture=sum(valor,na.rm=TRUE))

siconfi_agg<-siconfi_agg%>%
  left_join(infra, by=c("id_municipio", "ano"))%>%
  left_join(energy, by=c("id_municipio", "ano"))%>%
  left_join(environ, by=c("id_municipio", "ano"))%>%
  left_join(industry_commerce, by=c("id_municipio", "ano"))%>%
  left_join(housing, by=c("id_municipio", "ano"))%>%
  left_join(social_assistance, by=c("id_municipio", "ano"))%>%
  left_join(social_security, by=c("id_municipio", "ano"))%>%
  left_join(health, by=c("id_municipio", "ano"))%>%
  left_join(labor, by=c("id_municipio", "ano"))%>%
  left_join(education, by=c("id_municipio", "ano"))%>%
  left_join(agriculture, by=c("id_municipio", "ano"))

#remove intermediate tables  
rm(list=setdiff(ls(), c("panel", "siconfi_agg")))

siconfi_agg <- siconfi_agg %>%ungroup()%>%
  mutate(across(3:14, ~replace_na(.x, 0)))


#Deflate
ipca<-readRDS(here("raw","ipca_deflator.RDS"))
ipca <- type.convert(ipca, as.is = TRUE) 
siconfi_agg<-siconfi_agg%>%left_join(ipca, by=c("ano"))


siconfi_agg<-siconfi_agg %>%mutate_at(c(3:14), ~.*deflator)%>%select(-deflator)

#join with panel (full join because previous data set only have data until 2022, here 2023 data for first time)
panel<-siconfi_agg%>%full_join(panel, by=c("id_municipio","ano"))
rm(siconfi_agg)
```
6. merge SICONFI receipts data
```{r}
#load receipts data
siconfi_receipts<-readRDS(here("raw","siconfi_receipts.RDS"))

#adapt class for merge
siconfi_receipts <- type.convert(siconfi_receipts, as.is = TRUE) 

check_cats<-siconfi_receipts%>%ungroup()%>%distinct(conta_bd, portaria)

transfer_conv<-siconfi_receipts%>%filter(str_detect(conta_bd,"^Transferência de Convênios$"))%>%arrange(id_municipio,ano, portaria)

#Before 2013, deductions are registered under "Deduções da Receita Corrente", then afterwards they are dealt with at the item-level with a separate category under "estagio"
estagio_year<-siconfi_receipts%>%distinct(estagio_bd,ano)
deducoes <- siconfi_receipts %>%
  filter(str_detect(conta_bd, regex("dedu", ignore_case = TRUE)))%>%distinct(estagio_bd, conta_bd,ano)

#Replace phase and account names for deductions of current account pre-2012, so they will automatically be deducted in netting process (see next)
siconfi_receipts <- siconfi_receipts %>%
  mutate(estagio_bd = if_else(conta_bd == "Deduções da Receita Corrente", "Outras Deduções da Receita", estagio_bd),
         conta_bd = if_else(conta_bd == "Deduções da Receita Corrente", "Receitas Correntes", conta_bd))

remove(estagio_year, deducoes)

#Turn gross receipts into net receipts by subtracting the deductions
siconfi_receipts<-siconfi_receipts%>%
  mutate(value=if_else(estagio_bd=="Receitas Brutas Realizadas",valor,-valor))

siconfi_receipts_net<-siconfi_receipts%>%
  group_by(id_municipio,ano, conta_bd)%>%
  summarize(net_value=sum(value,na.rm=TRUE))
remove(siconfi_receipts)


#filter out categories of interest
cats <- c("^Receitas Correntes$", 
          "^Impostos, Taxas e Contribuições de Melhoria$", 
          "^Impostos$", 
          "^Imposto sobre a Propriedade Predial e Territorial Urbana - IPTU$", 
          "^Imposto sobre Transmissão Inter Vivos de Bens Imóveis e de Direitos Reais sobre Imóveis - ITBI$", 
          "^Imposto sobre Serviços de Qualquer Natureza - ISSQN$", 
          "^Receitas Patrimoniais$", 
          "^Receitas Industriais$", 
          "^Receitas de Serviços$", 
          "^Transferências Correntes$", 
          "^Receitas de Capital$", 
          "^Alienação de Bens$", 
          "^Transferências de Capital$", 
          "^Transferências Intergovernamentais*", 
          "^Receitas Correntes - Intraorçamentárias$", 
          "^Receitas de Capital - Intraorçamentárias$",
          "^Transferências de Instituições Privadas$",
          "^Transferências de Pessoas$",
          "^Transferências do Exterior$",
          "^Transferências dos Estados e do Distrito Federal e de suas Entidades$",
          "^Transferências de Outras Instituições Públicas$",
          "^Transferências da União e de suas Entidades$",
          "^Demais Transferências Correntes$",
          "^Transferências da União$",
          "^Transferências dos Estados$",
          "^Transferências dos Municípios$",
          "^Cota-Parte do Fundo de Participação dos Municípios - FPM$",
          "^Cota-Parte do ICMS$", 
          "^Participação na Receita dos Estados e Distrito Federal$", 
          "^Participação na Receita dos Estados$", 
          "^Participação na Receita da União$",
          "$Cota-Parte (IPI - Exportação)$",
          "^Cota-Parte do IPI - Municípios$")



siconfi_receipts_net_reduced<-siconfi_receipts_net%>%
  filter(str_detect(conta_bd,paste(cats, collapse = "|")))

#provide new var names for categories of interest and merge slightly different name of category intergovernmental transfer prior 2002
cats_final<-siconfi_receipts_net_reduced%>%ungroup()%>%distinct(conta_bd)

cats_short<-c("asset_sales_capital", "share_fpm", "share_icms", "service_tax","itbi","iptu","taxes","taxes_fees","current_receipts","industrial_receipts_current",
              "asset_receipts_current","capital_receipts", "service_receipts_current","current_transfers","intergov_transfers","intergov_transfers","transfers_federal",  "capital_transfers", "transfers_state",  "intergov_transfers", "transfer_private", "transfer_otherpublic", "transfer_persons", "transfer_exterior","transfer_municip", "participation_federal_receipts", "participation_state_receipts", "current_intrabudg", "capital_intrabudg", "share_ipi", "transfers_federal", "transfers_state","participation_state_receipts", "other_current_transfers")

cats_merge <- data.frame(
  conta_bd = cats_final,
  cats_short = cats_short
)

siconfi_receipts_final<-siconfi_receipts_net_reduced%>%
  left_join(cats_merge, by="conta_bd")%>%
  group_by(cats_short,ano,id_municipio)%>%
  summarize(net_value=sum(net_value,na.rm = TRUE))

nas<-siconfi_receipts_final%>%filter(is.na(net_value))
  

remove(siconfi_receipts_net,siconfi_receipts_net_reduced)

#deflate
ipca<-readRDS(here("raw","ipca_deflator.RDS"))
ipca <- type.convert(ipca, as.is = TRUE) 
siconfi_receipts_final<-siconfi_receipts_final%>%left_join(ipca, by=c("ano"))
siconfi_receipts_final<-siconfi_receipts_final %>%mutate(net_value=net_value*deflator)%>%select(1,2,3,4)


#bring into wide format for merge with panel data set 
siconfi_receipts_final_wide <- siconfi_receipts_final %>%
  pivot_wider(names_from = cats_short, 
              values_from = net_value,
              id_cols = c(ano, id_municipio))

#replace NA (years where nothing for this budget category was recorded) to zeros
siconfi_receipts_final_wide <- siconfi_receipts_final_wide %>%
  mutate_all(~replace(., is.na(.), 0))

#create total budgetary and total receipts
siconfi_receipts_final_wide<-siconfi_receipts_final_wide%>%
  mutate(total_receipts_excl_intrab=current_receipts+capital_receipts, 
         total_intrabudget=current_intrabudg+capital_intrabudg, 
         total_receipt_BRL2020=total_receipts_excl_intrab+total_intrabudget)


panel<-panel%>%full_join(siconfi_receipts_final_wide, by=c("id_municipio","ano"))

#save intermediate panel
saveRDS(panel, here("intermediate", "panel_intermediate.RDS"))
rm(list=ls())
```

```{r}
panel<-readRDS(here("intermediate", "panel_intermediate.RDS"))
distinct<-panel%>%group_by(id_municipio,ano)%>%summarise(n=n())%>%filter(n>1)

outages<-readRDS(here("intermediate","outages_2017_2022.RDS"))%>%filter(!is.na(CodMunicipio))

#do full join to add the year 2022 to the data (does not yet exist)
panel<-panel%>%full_join(outages, by=c("id_municipio"="CodMunicipio","ano"="Ano"))

#Complete static information for year 2022 and delete incomplete name data
panel<-panel%>%group_by(id_municipio)%>%tidyr::fill(c("sigla_uf","ibge_6d"))%>%select(-municipality_name)
```


7. add geographic data and names of municipalities
```{r}
municipalities<-readRDS(here("raw","geodata_municipios.RDS"))%>%select(-3)
municipalities <- type.convert(municipalities, as.is = TRUE) 


panel<-panel%>%left_join(municipalities, by=c("id_municipio"))
nonames<-panel%>%filter(is.na(nome_municipio))

#manually add the names
panel$nome_municipio[panel$id_municipio==1504752]<-"Mojuí dos Campos"
panel$nome_municipio[panel$id_municipio==4212650]<-"Pescaria Brava"
panel$nome_municipio[panel$id_municipio==4220000]<-"Balneário Rincão"
panel$nome_municipio[panel$id_municipio==4314548]<-"Pinto Bandeira"
panel$nome_municipio[panel$id_municipio==5006275]<-"Paraíso das Águas"

#drop municipality_id=4314530 (wrong ID added through full join by outage data)
panel<-panel%>%filter(id_municipio!="4314530")

panel<-panel%>%rename(municipality_name=nome_municipio)
```


8. Solar Irradiation
```{r}
`%notin%` <- Negate(`%in%`)
irradiation<-fread(here("raw","global_horizontal_means_sedes-munic.csv"))
names(irradiation) <- tolower(names(irradiation))
irradiation$state<-tolower(irradiation$state)
uf<-read_excel(here("raw","uf.xlsx"))
uf$`estado `<-tolower(uf$`estado `)
uf<-uf%>%rename(state=`estado `)
irradiation<-stringdist_join(irradiation, uf,
                   by           = "state",
                   mode         = "left",
                   ignore_case  = FALSE, 
                   method       = "jw", 
                   max_dist     = 0.08,
                  distance_col = "dist")
irradiation<-irradiation%>%mutate(municipio_state=paste(name, Sigla, sep = "-"))
irradiation<-irradiation%>%rename(irradiation_2017=annual)
irradiation<-irradiation%>%select(municipio_state, irradiation_2017, lon, lat)
irradiation$municipio_state<-str_trim(irradiation$municipio_state)
panel$municipality_name<-str_trim(panel$municipality_name)
panel<-panel%>%mutate(municipio_state=paste(municipality_name,sigla_uf,sep = "-"))

panel<-panel%>%ungroup()
panel<-panel%>%mutate(row_id=row_number())
panel<-stringdist_join(panel, irradiation,
                   by           = "municipio_state",
                   mode         = "left",
                   ignore_case  = FALSE, 
                   method       = "jw", 
                   max_dist     = 0.13,
                  distance_col = "dist")%>%
                  group_by(row_id) %>%
                slice_min(dist, n=1, with_ties=FALSE)

#Panel is reduced because five duplicates were in the previous version of "panel"
duplicates<-panel%>%group_by(id_municipio,ano)%>%filter(n()>1) %>%
  ungroup()

#now not anymore
panel<-panel%>%ungroup()
panel_distinct<-panel%>%distinct(id_municipio,ano,.keep_all=TRUE)

#delete longitude and latitude which are incomplete (8 missing) and add this info from other file
panel_distinct<-panel_distinct%>%select(-dist,-lon,-lat)

geo<-read.csv(here("intermediate","municipios.csv"))%>%select(codigo_ibge,latitude,longitude)%>%
  rename(lon=longitude, 
         lat=latitude)

panel_distinct<-panel_distinct%>%left_join(geo, by=c("id_municipio"="codigo_ibge"))
#no missing values
missing<-panel_distinct%>%filter(is.na(lon))

# 4 municipalities have no irradiation values, take the irradiation values from nearest municipality
no_irr<-panel_distinct%>%filter(is.na(irradiation_2017))%>%distinct(id_municipio, lon,lat)
all_mun<-panel_distinct%>%filter(id_municipio %notin% no_irr$id_municipio)%>%distinct(id_municipio, lon,lat, irradiation_2017)

library(geosphere)
dist_matrix <- distm(no_irr[,c("lon", "lat")], all_mun[,c("lon", "lat")], fun=distGeo)

# Find the index of the closest municipality to each row in 'no_irr'
closest_mun <- apply(dist_matrix, 1, which.min)

# Get the corresponding 'id_municipio' for the closest municipality
closest_mun <- as.numeric(closest_mun)
closest_municipality <- all_mun$id_municipio[closest_mun]

# Add the 'closest_municipality' column to 'no_irr'
no_irr$closest_municipality <- closest_municipality

no_irr<-no_irr%>%left_join(all_mun, by=c("closest_municipality"="id_municipio"))
                          
# Replace NA values in 'panel$irradiation_2017' with corresponding values from 'no_irr$irradiation_2017'
panel_distinct$irradiation_2017[is.na(panel_distinct$irradiation_2017)] <- no_irr$irradiation_2017[match(panel_distinct$id_municipio[is.na(panel_distinct$irradiation_2017)], no_irr$id_municipio)]

check<-panel_distinct%>%filter(id_municipio %in% no_irr$id_municipio)%>%distinct(id_municipio, irradiation_2017)

#Save
saveRDS(panel_distinct,here("intermediate","panel_v2.RDS"))
rm(list=ls())
```

9. Adding jobs from outside the municipality
```{r}
panel2<-readRDS(here("intermediate","panel_v2.RDS"))%>%arrange(id_municipio,ano)
jobs_from_outside<-readRDS(here("raw","jobs_from_outside.RDS"))

#adapt class for merge
jobs_from_outside <- type.convert(jobs_from_outside, as.is = TRUE)
#left joining them to panel dataset
panel2<-panel2%>%left_join(jobs_from_outside, by=c("id_municipio"="id_municipio_trabalho","ano"))

#Data only available 2005-2011 and 2017-2021. NAs in these periods are instances were there were no externally registered workers work in this municipality, 
# so can replace with zeros ( we know this because there are )

nas<-panel2%>%filter(ano %in%c(2005:2011)& jobs_from_outside==0)
panel2$jobs_from_outside[is.na(panel2$jobs_from_outside)& panel2$ano<2012 & panel2$ano>2004]<-0
panel2$jobs_from_outside3112[is.na(panel2$jobs_from_outside3112)& panel2$ano<2012 & panel2$ano>2004]<-0
panel2$jobs_from_outside[is.na(panel2$jobs_from_outside)& panel2$ano<2023 & panel2$ano>2016]<-0
panel2$jobs_from_outside3112[is.na(panel2$jobs_from_outside3112)& panel2$ano<2023 & panel2$ano>2016]<-0

panel2<-panel2%>%mutate(share_ext_jobs3112=jobs_from_outside3112/(total_jobs_3112+jobs_from_outside3112))
```

10. Check annual GDP data, correct data entry errors and then deflate GDP plus wage and revenue data
```{r}
pib<-readRDS(here("raw","pib.RDS"))
pib <- type.convert(pib, as.is = TRUE)

#load the 2021 manually from the IBGE website (https://www.ibge.gov.br/estatisticas/economicas/contas-nacionais/9088-produto-interno-bruto-dos-municipios.html?=&t=downloads)
pib_2021<-read_excel(here("raw","pib_mun.xlsx"))%>%filter(Ano=="2021")%>%select(1,7,33:39)
pib_2021<-pib_2021%>%
  rename(ano=1,
         id_municipio=2, 
         va_agropecuaria=3,
         va_industria=4,
         va_servicos=5,
         va_adespss=6,
         va=7,
         impostos_liquidos=8,
         pib=9
         )
#converts from thousands BRL to BRL
pib_2021[, 3:9] <- pib_2021[, 3:9] * 1000
pib_2021$ano<-as.integer(pib_2021$ano)
pib_2021$id_municipio<-as.integer(pib_2021$id_municipio)

pib<-bind_rows(pib,pib_2021)
options(scipen = 999)

#take out 2002 because of bad data
pib<-pib%>%filter(ano>2002)
pib<-pib%>%
  mutate(pib2=va+impostos_liquidos)%>%
  mutate(check1=pib-(va+impostos_liquidos))%>%
  mutate(check2=va-(va_agropecuaria+va_industria+va_servicos+va_adespss))

#there are many occassion where they forgot to add 1 or 2 zeros, identify those
pib<-pib%>%mutate(pib_multiple=round(pib2/pib,0))%>%
  mutate(va_multiple=round((va_agropecuaria+va_industria+va_servicos+va_adespss)/va))


#cases where they forgot 1 or multiple zeros on the PIB
pib<-pib%>%mutate(pib_clean=if_else(pib_multiple==10, pib*10,
                              if_else(pib_multiple==100, pib*100,
                                      if_else(pib_multiple==1000,pib*1000,0))))

#cases where the total value added lack one or multiple zeros
pib<-pib%>%mutate(va_clean=if_else(va_multiple==10, va*10,
                              if_else(va_multiple==100, va*100,
                                      if_else(va_multiple==1000,va*1000,0))))

#where VA total lacks zero take va sum of its parts
pib <- pib%>%
  mutate(pib_clean = ifelse(va_clean != 0 & pib_clean==0, va_clean + impostos_liquidos, pib_clean))

#for remaining cases take original value
pib$pib_clean[pib$pib_clean==0]<-pib$pib[pib$pib_clean==0]


#After this check for remaining "unrealistic" year-to-year changes
pib<-pib%>%arrange(id_municipio,ano)%>%
  group_by(id_municipio)%>%
  mutate(change=(pib_clean-lag(pib_clean,1))/lag(pib_clean,1)*100)%>%
  mutate(change_lag2=(pib_clean-lag(pib_clean,2))/lag(pib_clean,2)*100)%>%
  mutate(abs_change=abs((pib_clean-lag(pib_clean,1))/lag(pib_clean,1)*100))%>%ungroup()

length(pib$check1[pib$check1==0])/length(pib$check1)
pib<-pib%>%mutate(check1_new=pib_clean-(va+impostos_liquidos))
length(pib$check1_new[pib$check1_new==0])/length(pib$check1_new)


#wherever the change in GDP was by more than 85% take VA+tax rather than PIB
pib2<-pib%>%mutate(pib_clean = if_else(abs_change>85 & !is.na(abs_change), pib2, pib_clean))

#re-do lag operation to check
pib2<-pib2%>%arrange(id_municipio,ano)%>%
  group_by(id_municipio)%>%
  mutate(change=(pib_clean-lag(pib_clean,1))/lag(pib_clean,1)*100)%>%
  mutate(change_lag2=(pib_clean-lag(pib_clean,2))/lag(pib_clean,2)*100)%>%
  mutate(abs_change=abs((pib_clean-lag(pib_clean,1))/ lag(pib_clean,1)*100))


big_errors2<-pib2%>%filter(abs_change>30)
big_errors1<-pib%>%filter(abs_change>30)

#Finally: try to reduce errors through re-calculating PIB with the individual elements provided
pib2<-pib2%>%mutate(pib3=(va_agropecuaria+va_industria+va_servicos+va_adespss+impostos_liquidos))

pib3<-pib2%>%mutate(pib_clean = if_else(abs_change>30 & !is.na(abs_change), pib3, pib_clean))
pib3<-pib3%>%arrange(id_municipio,ano)%>%
  group_by(id_municipio)%>%
  mutate(change=(pib_clean-lag(pib_clean,1))/lag(pib_clean,1)*100)%>%
  mutate(change_lag2=(pib_clean-lag(pib_clean,2))/lag(pib_clean,2)*100)%>%
  mutate(abs_change=abs((pib_clean-lag(pib_clean,1))/lag(pib_clean,1)*100))%>%
  mutate(abs_change_lag2=abs((pib_clean-lag(pib_clean,2))/lag(pib_clean,2)*100))

ggplot(pib3%>%filter(abs_change<10000), aes(x=abs_change))+geom_histogram()+scale_x_continuous(breaks = seq(0,200,10))

#
big_errors3<-pib3%>%filter(abs_change>70 & abs_change_lag2>70)



municipalities_problem<-big_errors3%>%filter(abs_change>50)%>%group_by(id_municipio)%>%
  summarise(count=n())


municipalities<-pib3%>%filter(ano<2007)%>%filter(abs_change>50)%>%group_by(id_municipio)%>%summarise(count=n())%>%filter(count>1)

`%notin%` <- Negate(`%in%`)

#replace very unrealistic values (negative) or large y-o-y changes (above 80% compared to previous last years ) with NAs
pib3$pib_clean[pib3$abs_change>=80 & pib3$abs_change_lag2>=80]<-NA
pib3$pib_clean[pib3$pib_clean<0]<-NA

#check sector specific data for big y-o-y changes
pib3<-pib3%>%arrange(id_municipio,ano)%>%
  group_by(id_municipio)%>%
  mutate(abs_change_agr=abs((va_agropecuaria-lag(va_agropecuaria,1))/lag(va_agropecuaria,1)*100))%>%
  mutate(abs_change_ind=abs((va_industria-lag(va_industria,1))/lag(va_industria,1)*100))%>%
  mutate(abs_change_servicos=abs((va_servicos-lag(va_servicos,1))/lag(va_servicos,1)*100))%>%
  mutate(abs_change_public=abs((va_adespss-lag(va_adespss,1))/lag(va_adespss,1)*100))%>%
  mutate(abs_change_agr_lag2=abs((va_agropecuaria-lag(va_agropecuaria,2))/lag(va_agropecuaria,2)*100))%>%
  mutate(abs_change_ind_lag2=abs((va_industria-lag(va_industria,2))/lag(va_industria,2)*100))%>%
  mutate(abs_change_servicos_lag2=abs((va_servicos-lag(va_servicos,2))/lag(va_servicos,2)*100))%>%
  mutate(abs_change_public_lag2=abs((va_adespss-lag(va_adespss,2))/lag(va_adespss,2)*100))

ggplot(pib3%>%filter(abs_change_agr_lag2<200), aes(x=abs_change_agr_lag2))+geom_histogram()+scale_x_continuous(breaks = seq(0,200,10))

#similar to overall GDP, spike in histogram suggests that if change is 80+ percent for both lags then it is very likely data entry and will be turned into NA
pib3<-pib3%>%mutate(va_agropecuaria=if_else((abs_change_agr>=80 & abs_change_agr_lag2>=80), NA,va_agropecuaria))%>%
  mutate(va_industria=if_else((abs_change_ind>=80 & abs_change_ind_lag2>=80), NA,va_industria))%>%
  mutate(va_servicos=if_else((abs_change_servicos>=80 & abs_change_servicos_lag2>=80), NA,va_servicos))%>%
  mutate(va_adespss=if_else((abs_change_public>=80 & abs_change_public_lag2>=80), NA,va_adespss))

pib_final<-pib3%>%select(id_municipio, ano, pib_clean,va_agropecuaria,va_industria,va_servicos,va_adespss)


#deflate the data
#Deflate
ipca<-readRDS(here("raw","ipca_deflator.RDS"))
ipca <- type.convert(ipca, as.is = TRUE) 

pib_final<-pib_final%>%left_join(ipca, by="ano")%>%
  mutate(pib_clean_constant2020_BRL=pib_clean*deflator)%>%
  mutate(va_industria_constant2020_BRL=va_industria*deflator)%>%
  mutate(va_agropecuaria_constant2020_BRL=va_agropecuaria*deflator)%>%
  mutate(va_adespss_constant2020_BRL=va_adespss*deflator)%>%
  mutate(va_servicos_constant2020_BRL=va_servicos*deflator)

panel2<-panel2%>%left_join(pib_final, by=c("id_municipio","ano"))
rm(list=setdiff(ls(), c("panel2")))
```

12. add the wind speed data
```{r}
wind<-readRDS(here("intermediate","wind_municipalities.RDS"))%>%select(codigo_ibge, station_code, avg_wind_speed)
panel2<-panel2%>%left_join(wind, by=c("id_municipio"="codigo_ibge"))
```

10. merge power plant information
```{r}
plants<-readRDS(here("intermediate","plants_municipality_year.RDS"))

panel2$ano<-as.integer(panel2$ano)
plants$year_operation<-as.integer(plants$year_operation)
plants$mun_id<-as.integer(plants$mun_id)

panel2<-panel2%>%left_join(plants, by=c("ano"="year_operation", "id_municipio"="mun_id"))

#transform all the NAs of the new matched columns to zeros (municipalities without power plants)
panel2 <- panel2 %>%
  mutate(across(starts_with(c("no_plants", "mw_operation", "new_mw", "total_new", "total_mw", "mw_cum", "cum_no","bndes_")),
                ~if_else(is.na(.), 0, .)))


# so far BNDES dummies only in respective year not for all municipality-years
bndes_check<-panel2%>%filter(bndes_supported==1)%>%select(id_municipio, ano, new_mw_solar, new_mw_wind, bndes_lcr, bndes_supported)
#create bndes_municipality and lcr_municipality markers
panel2<-panel2%>%
  group_by(id_municipio)%>%
  mutate(lcr_municipality=if_else(any(bndes_lcr==1),1,0))%>%
  mutate(bndes_municipality=if_else(any(bndes_supported==1),1,0))
rm(list=setdiff(ls(), c("panel2")))
```


11. merge firm creation data
```{r}
firm_creation_annual<-readRDS(here("raw","cnpj_cnae_month_year_2005_2022.RDS"))

#adapt class for merge
firm_creation_annual <- type.convert(firm_creation_annual, as.is = TRUE)

firm_creation_year<-firm_creation_annual%>%
  group_by(id_municipio,year)%>%
  summarise(new_establishments=sum(establishments_founded), 
            new_mother_companies=sum(mother_companies_founded))%>%ungroup()
expand<-firm_creation_year%>%tidyr::expand(id_municipio, year)
expand<-left_join(expand, firm_creation_year, by=c("id_municipio","year"))
expand<-expand%>%filter(!is.na(id_municipio))
expand$new_establishments[is.na(expand$new_establishments)]<-0
expand$new_mother_companies[is.na(expand$new_mother_companies)]<-0

wind_codes<-read_excel(here("raw", "wind_solar_cnae.xlsx"), sheet = "wind_related cnae")
solar_codes<-read_excel(here("raw", "wind_solar_cnae.xlsx"), sheet ="solar_related_CNAE_")


wind_firms<-firm_creation_annual%>%
  filter(cnae_fiscal_principal %in% wind_codes$cnae)%>%
  group_by(id_municipio, year)%>%
  summarise(no_establishments_wind=sum(establishments_founded,na.rm = TRUE),
            mother_companies_wind=sum(mother_companies_founded,na.rm = TRUE),
            foreign_establishment_wind=sum(foreign_owned_establishment,na.rm = TRUE))

solar_firms<-firm_creation_annual%>%
  filter(cnae_fiscal_principal %in% solar_codes$cnae)%>%
  group_by(id_municipio, year)%>%
  summarise(no_establishments_solar=sum(establishments_founded,na.rm = TRUE),
            mother_companies_solar=sum(mother_companies_founded,na.rm = TRUE),
            foreign_establishment_solar=sum(foreign_owned_establishment,na.rm = TRUE))


#Since 2022 is already present left_join is sufficient
panel2<-panel2%>%
  left_join(wind_firms,by=c("id_municipio", "ano"="year"))

panel2<-panel2%>%
  left_join(solar_firms, by=c("id_municipio", "ano"="year"))
panel2<-panel2%>%
  left_join(expand, by=c("id_municipio", "ano"="year"))


nas<-panel2%>%filter(is.na(new_mother_companies) , is.na(new_establishments))%>%select(id_municipio,ano, starts_with(c("new_mother_companies","new_establishments")))%>%
  ungroup()%>%distinct(ano)

#nas only pre-2005 because before no data collected
remove(nas)
#Save
saveRDS(panel2,here("intermediate","panel_v3.RDS"))
rm(list=ls())

```

10. add distance to power plant
```{r}
annual_panel<-readRDS(here("intermediate","panel_v3.RDS"))%>%arrange(id_municipio, ano)
#first identify all municipalities where more than 5MW were installed of any type since 2004 (to leave enough gap until we start observing labour data in 2007)
mw_larger5_location<-annual_panel%>%group_by(id_municipio)%>%filter(any(new_mw_other>5|new_mw_solar>5|new_mw_wind>5) & ano>2004)%>%select(starts_with("new_mw"),ano, id_municipio,lon,lat)%>%distinct(id_municipio,lon,lat)

all_mun<-annual_panel%>%distinct(id_municipio,lon,lat)
library(geosphere)


# calculate the distance matrix between municipalities with power power plants and all municipalities
dist_matrix <- distm(mw_larger5_location[,c("lon", "lat")], all_mun[,c("lon", "lat")], fun=distGeo)

# find the index of the closest power plant to each municipality
plant_5MW_distance <- apply(dist_matrix, 2, function(x) min(x))

# add the station_code column to the municipalities dataframe
all_mun$plant_5MW_distance <- plant_5MW_distance
all_mun<-all_mun%>%mutate(plant_5MW_distance=plant_5MW_distance/1000)

#test whether all station that have power plant have distance zero
test<-all_mun%>%left_join(mw_larger5_location, by=c("id_municipio"))
remove(test)
#check if there are sufficient control municipalities in each state
states<-annual_panel%>%distinct(id_municipio,sigla_uf)
larger50<-all_mun%>%filter(plant_5MW_distance>50)%>%left_join(states, by=c("id_municipio"))
distinct<-larger50%>%ungroup()%>%group_by(sigla_uf)%>%summarise(no_mun=n_distinct(id_municipio))
larger40<-all_mun%>%filter(plant_5MW_distance>40)
remove(states,larger50,distinct,larger40)


#add distance to solar and wind plants as well to be later used as spillover dummies
solar_larger5_location<-annual_panel%>%group_by(id_municipio)%>%filter(any(new_mw_solar>5) & ano>2006)%>%select(new_mw_solar,ano, id_municipio,lon,lat)%>%distinct(id_municipio,lon,lat)
dist_matrix_solar <- distm(solar_larger5_location[,c("lon", "lat")], all_mun[,c("lon", "lat")], fun=distGeo)
solarplant_5MW_distance <- apply(dist_matrix_solar, 2, function(x) min(x))

all_mun$solarplant_5MW_distance <- solarplant_5MW_distance
all_mun<-all_mun%>%mutate(solarplant_5MW_distance=solarplant_5MW_distance/1000)

wind_larger5_location<-annual_panel%>%group_by(id_municipio)%>%filter(any(new_mw_wind>5) & ano>2006)%>%select(new_mw_wind,ano, id_municipio,lon,lat)%>%distinct(id_municipio,lon,lat)
dist_matrix_wind <- distm(wind_larger5_location[,c("lon", "lat")], all_mun[,c("lon", "lat")], fun=distGeo)
windplant_5MW_distance <- apply(dist_matrix_wind, 2, function(x) min(x))
all_mun$windplant_5MW_distance <- windplant_5MW_distance
all_mun<-all_mun%>%mutate(windplant_5MW_distance=windplant_5MW_distance/1000)


all_mun<-all_mun%>%select(-c("lon","lat"))
annual_panel<-annual_panel%>%left_join(all_mun, by="id_municipio")
```

add distance to coastline:https://stackoverflow.com/questions/51837454/r-measuring-distance-from-a-coastline 
```{r}
geopacks<-c("sf", "geosphere", "rnaturalearth","rnaturalearthdata", "mapdata")

lon_lat<-annual_panel%>%ungroup()%>%distinct(id_municipio,lon, lat)
# Filter out rows with missing lon or lat values
lon_lat <- lon_lat %>% filter(!is.na(lon) & !is.na(lat))

lons<-lon_lat$lon
lats<-lon_lat$lat

#use dist2coast funtion from: https://github.com/Davidatlarge/dist2coast/blob/main/README.md 
dist2coast <- function(lons,
                       lats,
                       coastline_crop = NULL, #  numeric vector with xmin, ymin, xmax and ymax for cropping the coastline to a bounding box, e.g. c(xmin = -1, ymin = 50, xmax = 11, ymax = 60), elements do not have to be named but must be in the correct order
                       coastline = "ne", # coastline source; "ne" for Natural Earth (www.naturalearthdata.com) (faster), "mapdata" for using map('world') (more precise)
                       as_utm32 = FALSE, # transform both points and coast to UTM32, i.e. a planar projection, for more speed
                       spherical = FALSE, # operations using coastline = "mapdata" may fail if spherical (S2) processing is used
                       output = "mindist", # "mindist" for distance to nearest coastline, "distmat" for matrix of distances between points (in rows) and every line (in cols)
                       plot = FALSE
                       
) {
  suppressWarnings( suppressPackageStartupMessages(library(dplyr, quietly = TRUE)) )
  suppressWarnings( suppressPackageStartupMessages(library(mapdata, quietly = TRUE)) ) 
  suppressWarnings( suppressPackageStartupMessages(library(sf, quietly = TRUE)) )
  
  old_sf_use_s2 <- sf::sf_use_s2() # save setting to restore it at the end
  suppressMessages( sf::sf_use_s2(spherical) ) # several operations do not work with S2 processing
  
  # make sf features for points and coastline
  points <- data.frame(lons, lats) %>%
    st_as_sf(coords = c("lons", "lats")) %>%
    st_set_crs(4326)
  
  switch(coastline,
         "ne" = coast <- rnaturalearth::ne_coastline(scale = 110, returnclass = "sf") %>% st_set_crs(4326),
         "mapdata" = coast <- st_as_sf(map('world', plot = FALSE, fill = TRUE)) %>% st_set_crs(4326)
  )
  
  # crop coastline
  if(!is.null(coastline_crop)) {
    if(is.null(names(coastline_crop))) {names(coastline_crop) <- c("xmin", "ymin", "xmax", "ymax")}
    suppressMessages(suppressWarnings(
      coast <- st_crop(coast, coastline_crop)
    ))
  }
  
  # transform to UTM 32
  if(as_utm32) {
    points <- points %>% st_transform(25832)
    coast <- coast %>% st_transform(25832)
  }
  
  # calculate distances
  distmat <- st_distance(points, coast)
  mindist <- apply(distmat, 1, min)
  
  switch (output,
          "mindist" = out <- mindist,
          "distmat" = out <- distmat)
  
  if(plot) {
    suppressWarnings(library(ggplot2, quietly = TRUE))
    p1 <- ggplot() +
      geom_sf(data = coast, fill = "grey70") +
      geom_point(aes(lons, lats, col = mindist/1000)) +
      scale_x_continuous(expand = c(0,0)) +
      scale_y_continuous(expand = c(0,0)) +
      scale_color_gradientn(name = "distance to\nshore [km]", colours = c("blue", "red")) +
      theme_bw()
    print(p1)
  }
  
  suppressMessages( sf::sf_use_s2(old_sf_use_s2) ) # restore setting
  
  return(out)
}

dist<-dist2coast(lons,lats, coastline = "ne")
#divide by 1000 to have distance in km
lon_lat$coast_dist<-dist/1000
lon_lat<-lon_lat%>%mutate(at_coast=if_else(coast_dist<=20, 1,0))%>%select(id_municipio, coast_dist, at_coast)

#merge back to annual_panel data
annual_panel<-annual_panel%>%left_join(lon_lat, by=c("id_municipio"))
```


11. add per-capita measures for GDP, spending and receipts
```{r}
annual_panel<-annual_panel%>%mutate(spending_pc=total_spending/populacao, 
                                    total_receipt_pc=total_receipt_BRL2020/populacao, 
                                    gdp_pc=pib_clean_constant2020_BRL/populacao)
```


11. drop municipalities without continuous job data
```{r}
`%notin%` <- Negate(`%in%`)
annual_panel<-annual_panel%>%filter(id_municipio %notin% c(4212650,4220000,1504752, 4314548,5006275,1504752,2206720,2101731, 2111672,0))

#assure data is distinct at municipality year level
annual_panel<-annual_panel%>%ungroup()%>%distinct(id_municipio,ano, .keep_all = TRUE)
```


12. add treatment lags
```{r}
#for pre-periods create leads
for (i in 1:8) {
  col_name <- paste0("d_solar_pre", i)
  annual_panel <- annual_panel %>%
    mutate(!!col_name := c(tail(new_mw_solar, -i), rep(0, i)))
}

#for post periods create lags
for (i in 1:8) {
  col_name <- paste0("d_solar_post", i)
  annual_panel <- annual_panel %>%
    mutate(!!col_name := c(rep(0, i), head(new_mw_solar, -i)))
}

#Wind:for pre-periods create leads
for (i in 1:8) {
  col_name <- paste0("d_wind_pre", i)
  annual_panel <- annual_panel %>%
    mutate(!!col_name := c(tail(new_mw_wind, -i), rep(0, i)))
}

#Wind:for post periods create lags
for (i in 1:8) {
  col_name <- paste0("d_wind_post", i)
  annual_panel <- annual_panel %>%
    mutate(!!col_name := c(rep(0, i), head(new_mw_wind, -i)))
}

library(stats)
#create reverse cumulative sum function for leads
revcumsum <- function(x){
  x <- rev(cumsum(rev(x)))
}

#create binned treatments lags and lead at the end of the observed event window
annual_panel$d_solar_pre8_bin <- ave(annual_panel$d_solar_pre8,annual_panel$id_municipio, FUN = revcumsum)
annual_panel$d_solar_pre7_bin <- ave(annual_panel$d_solar_pre7,annual_panel$id_municipio, FUN = revcumsum)
annual_panel$d_solar_post4_bin <- ave(annual_panel$d_solar_post4,annual_panel$id_municipio, FUN = cumsum)
annual_panel$d_solar_post3_bin <- ave(annual_panel$d_solar_post3,annual_panel$id_municipio, FUN = cumsum)

annual_panel$d_wind_pre8_bin <- ave(annual_panel$d_wind_pre8,annual_panel$id_municipio, FUN = revcumsum)
annual_panel$d_wind_pre7_bin <- ave(annual_panel$d_wind_pre7,annual_panel$id_municipio, FUN = revcumsum)
annual_panel$d_wind_post6_bin <- ave(annual_panel$d_wind_post6,annual_panel$id_municipio, FUN = cumsum)
annual_panel$d_wind_post5_bin <- ave(annual_panel$d_wind_post5,annual_panel$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of solar and wind in the data period
annual_panel<-annual_panel%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
annual_panel <- annual_panel %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$new_mw_solar > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_solar = NA_real_)
    } else {
      .x %>% mutate(t_solar = row_number() - switch_index)
    }
  })


#repeat for wind
annual_panel <- annual_panel %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$new_mw_wind > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_wind = NA_real_)
    } else {
      .x %>% mutate(t_wind = row_number() - switch_index)
    }
  })

saveRDS(annual_panel, here("final","annual_panel_final_nospillover.RDS"))
```


Create additional data required for matching
```{r}
annual_panel<-readRDS(here("final","annual_panel_final_nospillover.RDS"))
#Put NA in case population is zero somewhere
annual_panel$populacao[annual_panel$populacao==0]<-NA
annual_panel<-annual_panel%>%arrange(id_municipio,ano)
annual_panel <- annual_panel %>%
  group_by(id_municipio) %>%
  mutate(employment_growth = (total_jobs_3112 -  dplyr::lag(total_jobs_3112)) / dplyr::lag(total_jobs_3112) * 100)%>%
  mutate(population_growth = (populacao -  dplyr::lag(populacao)) /  dplyr::lag(populacao) * 100)%>%
  mutate(gdp_pc= pib_clean_constant2020_BRL/populacao)%>%
  mutate(gdp_pc_growth=(gdp_pc -  dplyr::lag(gdp_pc)) /  dplyr::lag(gdp_pc) * 100)%>%
  mutate(gdp_growth=(pib_clean_constant2020_BRL -  dplyr::lag(pib_clean_constant2020_BRL)) /  dplyr::lag(pib_clean_constant2020_BRL) * 100)%>%
  mutate(total_receipt_pc=total_receipt_BRL2020/populacao)%>%
  mutate(spending_pc=total_spending/populacao)%>%
  mutate(no_firms_pc=total_establishment/populacao)%>%
  mutate(wind_inst_growth= (wind_installation_jobs_3112_total- dplyr::lag(wind_installation_jobs_3112_total)) /dplyr::lag(wind_installation_jobs_3112_total)*100)%>%
   mutate(wind_comp_growth= (wind_component_jobs_3112_total- dplyr::lag(wind_component_jobs_3112_total)) /dplyr::lag(wind_component_jobs_3112_total)*100)%>%
  mutate(wind_om_growth= (wind_om_jobs_3112_total- dplyr::lag(wind_om_jobs_3112_total)) /dplyr::lag(wind_component_jobs_3112_total)*100)%>%
   mutate(solar_inst_growth= (solar_installation_jobs_3112_total- dplyr::lag(solar_installation_jobs_3112_total)) /dplyr::lag(solar_installation_jobs_3112_total)*100)%>%
     mutate(solar_comp_growth= (solar_component_jobs_3112_total- dplyr::lag(solar_component_jobs_3112_total)) /dplyr::lag(solar_component_jobs_3112_total)*100)%>%
  mutate(solar_om_growth= (solar_om_jobs_3112_total- dplyr::lag(solar_om_jobs_3112_total)) /dplyr::lag(solar_component_jobs_3112_total)*100)%>%
  mutate(wage_growth= (avg_wage_2020_BRL- dplyr::lag(avg_wage_2020_BRL))/ dplyr::lag(avg_wage_2020_BRL)*100)%>%
  ungroup()

#occasions where the growth variable is NaN mark as zero and where it goes from zero to some value mark as NA (Infinite)
growth_columns <- grep("growth", colnames(annual_panel), value = TRUE)

# Loop through the growth columns and replace NaN with 0 and infinite values with NA
for (col in growth_columns) {
  annual_panel[[col]][is.nan(annual_panel[[col]])] <- 0
  annual_panel[[col]][is.infinite(annual_panel[[col]])] <- NA
}


#create region category
annual_panel<-annual_panel%>%
  mutate(region=if_else(sigla_uf %in% c("AC","AM","RR","PA","AP","TO","RO"), "North",
                        if_else(sigla_uf %in% c("MA","PI","CE","RN","PB","PE","AL","SE","BA"),"Northeast",
                                if_else(sigla_uf %in% c("GO","DF","MT","MS"),"Centerwest",
                                if_else(sigla_uf %in% c("MG","ES","RJ","SP"), "Southeast","South")))))

#Pool of potential control group for both wind and solar are municipalities that never so far received a power station
municipios_control<-annual_panel%>%filter(ano==2022 & mw_cum_total==0 & plant_5MW_distance>=50)%>%ungroup()%>%distinct(id_municipio)%>%mutate(potential_control=1)

annual_panel<-annual_panel%>%
  left_join(municipios_control, by=c("id_municipio"))

#Create first-treatment year variable
annual_panel<-annual_panel%>%
  group_by(id_municipio)%>%
  mutate(year_first_treat_wind=if_else(t_wind==0, ano, NA),
         year_first_treat_solar=if_else(t_solar==0, ano, NA))%>%
  fill(year_first_treat_wind, .direction= "downup")%>%
  fill(year_first_treat_solar,  .direction= "downup")

#Re-adjust t_wind=0 for the 3 municipalities that have wind investments prior to 2008 to second treatment instance (to allow for enough pre-treatment)
adjusted <- annual_panel %>%filter(year_first_treat_wind <2008)%>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$new_mw_wind > 5)[2]
    if (is.na(switch_index)) {
      .x %>% mutate(t_wind = NA_real_)
    } else {
      .x %>% mutate(t_wind = row_number() - switch_index)
    }
  })

adjusted<-adjusted%>%select(id_municipio, ano, t_wind)

annual_panel <- annual_panel %>%
  left_join(adjusted, by = c("id_municipio", "ano")) %>%
  mutate(t_wind = coalesce(t_wind.y, t_wind.x)) %>%
  select(-t_wind.y, -t_wind.x)

#Re-define the year of first treatment variable with adaption t_wind for early-adopters
annual_panel<-annual_panel%>%
  group_by(id_municipio)%>%
  mutate(year_first_treat_wind=if_else(t_wind==0, ano, NA),
         year_first_treat_solar=if_else(t_solar==0, ano, NA))%>%
  fill(year_first_treat_wind, .direction= "downup")%>%
  fill(year_first_treat_solar,  .direction= "downup")


saveRDS(annual_panel, here("final","annual_panel_final_noweights.RDS"))
```


13. Create solar spillover data
```{r}
# Unload unnecessary packages to avoid conflicts. Get a list of all loaded packages
loaded_packages <- names(sessionInfo()$otherPkgs)

# Detach each non-system package
lapply(loaded_packages, function(pkg) {
  # Construct the package name for detachment
  pkg_name <- paste0("package:", pkg)
  
  # Detach the package
  if (pkg_name %in% search()) {
    detach(pkg_name, unload = TRUE, character.only = TRUE)
  }
})

revcumsum <- function(x){
  x <- rev(cumsum(rev(x)))
}
library(here)
annual_panel<-readRDS(here("final","annual_panel_final_noweights.RDS"))
library(sf)
library(tidyverse)
library(units)
`%notin%` <- Negate(`%in%`)
#create a dataframe with longitude and latitude of locations that have solar park larger 5 MW
 
mw_larger5_solar<-annual_panel%>%group_by(id_municipio)%>%filter(any(new_mw_solar>5) & ano>2004)%>%select(starts_with("new_mw"),ano, id_municipio,lon,lat)%>%distinct(id_municipio,lon,lat)
 

#create dataframe
 
all_mun<-annual_panel%>%distinct(id_municipio,lon,lat)%>%
  filter(id_municipio %notin% mw_larger5_solar$id_municipio)

# convert dataframes to sf objects
mw_larger5_solar <- st_as_sf(mw_larger5_solar, coords = c("lon", "lat"), crs = 4326)
all_mun <- st_as_sf(all_mun, coords = c("lon", "lat"), crs = 4326)

# Transform to Cartesian CRS for appropriate distance calculation
mw_larger5_solar <- st_transform(mw_larger5_solar, 3857)
all_mun <- st_transform(all_mun, 3857)

within_distance_list <- st_is_within_distance(all_mun, mw_larger5_solar, dist = set_units(20000, "meters"))

# Ensure that all elements of nearby_solar_list are non-empty or NA
nearby_solar_list <- lapply(within_distance_list, function(x) {
  nearby_solar_ids <- mw_larger5_solar$id_municipio[unlist(x)] 
  if (length(nearby_solar_ids) == 0) NA else nearby_solar_ids})

names(nearby_solar_list) <- all_mun$id_municipio

nearby_solar_df <- tibble(id_municipio = names(nearby_solar_list), nearby_solar = nearby_solar_list)

max_len <- max(map_int(nearby_solar_df$nearby_solar, length), na.rm = TRUE)

nearby_solar_df <- nearby_solar_df %>%
  mutate(data = map(nearby_solar, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "solar_"))

#rename variables for final spillover dataset
nearby_solar_df<-nearby_solar_df%>%select(1,3,4)%>%
  rename(solar_spillover20k_1=solar_1, 
         solar_spillover20k_2=solar_2)

#Re do for 20-40km radius
# Find all municipalities within 40km

within_40km_list <- st_is_within_distance(all_mun, mw_larger5_solar, dist = set_units(40000, "meters"))

# Find all municipalities within 20km
within_20km_list <- st_is_within_distance(all_mun, mw_larger5_solar, dist = set_units(20000, "meters"))

# Determine municipalities that are more than 20km but less than or equal to 40km away
nearby_solar_list2 <- mapply(function(x, y) {
  nearby_solar_ids_40km <- mw_larger5_solar$id_municipio[unlist(x)]
  nearby_solar_ids_20km <- mw_larger5_solar$id_municipio[unlist(y)]
  nearby_solar_ids <- setdiff(nearby_solar_ids_40km, nearby_solar_ids_20km)
  if (length(nearby_solar_ids) == 0) NA else nearby_solar_ids
}, within_40km_list, within_20km_list)

names(nearby_solar_list2) <- all_mun$id_municipio

nearby_solar_df2 <- tibble(id_municipio = names(nearby_solar_list2), nearby_solar = nearby_solar_list2)

max_len <- max(map_int(nearby_solar_df2$nearby_solar, length), na.rm = TRUE)

nearby_solar_df2 <- nearby_solar_df2 %>%
  mutate(data = map(nearby_solar, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "solar_"))

#rename variables for final spillover dataset
nearby_solar_df2<-nearby_solar_df2%>%arrange(desc(nearby_solar))%>%
  select(1,3,4,5,6)%>%
  rename(solar_spillover40k_1=solar_1, 
         solar_spillover40k_2=solar_2,
         solar_spillover40k_3=solar_3,
         solar_spillover40k_4=solar_4)

#Re do for 40-50km radius
# Find all municipalities within 40km
within_50km_list <- st_is_within_distance(all_mun, mw_larger5_solar, dist = set_units(50000, "meters"))

# Find all municipalities within 40km
within_40km_list <- st_is_within_distance(all_mun, mw_larger5_solar, dist = set_units(40000, "meters"))

# Determine municipalities that are more than 40km but less than or equal to 50km away
nearby_solar_list3 <- mapply(function(x, y) {
  nearby_solar_ids_50km <- mw_larger5_solar$id_municipio[unlist(x)]
  nearby_solar_ids_40km <- mw_larger5_solar$id_municipio[unlist(y)]
  nearby_solar_ids <- setdiff(nearby_solar_ids_50km, nearby_solar_ids_40km)
  if (length(nearby_solar_ids) == 0) NA else nearby_solar_ids
}, within_50km_list, within_40km_list)

names(nearby_solar_list3) <- all_mun$id_municipio

nearby_solar_df3 <- tibble(id_municipio = names(nearby_solar_list3), nearby_solar = nearby_solar_list3)

max_len <- max(map_int(nearby_solar_df3$nearby_solar, length), na.rm = TRUE)

nearby_solar_df3 <- nearby_solar_df3 %>%
  mutate(data = map(nearby_solar, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "solar_"))

#rename variables for final spillover dataset
nearby_solar_df3<-nearby_solar_df3%>%arrange(desc(nearby_solar))%>%
  select(1,3,4)%>%
  rename(solar_spillover50k_1=solar_1, 
         solar_spillover50k_2=solar_2)

years<-annual_panel%>%select(id_municipio, ano)


spillover_solar_df<-nearby_solar_df%>%
  left_join(nearby_solar_df2, by=("id_municipio"))%>%
  left_join(nearby_solar_df3, by=c("id_municipio"))
spillover_solar_df$id_municipio<-as.integer(spillover_solar_df$id_municipio)

spillover_solar_df<- spillover_solar_df%>%
  left_join(years, by=c("id_municipio"))

  
#getting the treatment assignment 
treatment<-annual_panel%>%select(id_municipio, ano, new_mw_solar, lcr_municipality, bndes_municipality)

spillover_solar_df_final<-spillover_solar_df%>%
  left_join(treatment, by=c("solar_spillover20k_1"="id_municipio","ano"), suffix=c("","_20k1"))%>%
  left_join(treatment, by=c("solar_spillover20k_2"="id_municipio","ano"), suffix=c("","_20k2"))%>%
  left_join(treatment, by=c("solar_spillover40k_1"="id_municipio","ano"), suffix=c("","_40k1"))%>%
  left_join(treatment, by=c("solar_spillover40k_2"="id_municipio","ano"), suffix=c("","_40k2"))%>%
  left_join(treatment, by=c("solar_spillover40k_3"="id_municipio","ano"), suffix=c("","_40k3"))%>%
  left_join(treatment, by=c("solar_spillover40k_4"="id_municipio","ano"), suffix=c("","_40k4"))%>%
  left_join(treatment, by=c("solar_spillover50k_1"="id_municipio","ano"), suffix=c("","_50k1"))%>%
  left_join(treatment, by=c("solar_spillover50k_2"="id_municipio","ano"), suffix=c("","_50k2"))

spillover_solar_df_final$solar_spillover_20k_MW <- rowSums(spillover_solar_df_final[, c('new_mw_solar', 'new_mw_solar_20k2')], na.rm = TRUE)
spillover_solar_df_final$solar_spillover_40k_MW <- rowSums(spillover_solar_df_final[, c('new_mw_solar_40k1', 'new_mw_solar_40k2','new_mw_solar_40k3','new_mw_solar_40k4')], na.rm = TRUE)
spillover_solar_df_final$solar_spillover_50k_MW <- rowSums(spillover_solar_df_final[, c('new_mw_solar_50k1', 'new_mw_solar_50k2')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_lcr_municipality_20k <- rowSums(spillover_solar_df_final[, c('lcr_municipality', 'lcr_municipality_20k2')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_lcr_municipality_40k <- rowSums(spillover_solar_df_final[, c('lcr_municipality_40k1', 'lcr_municipality_40k2','lcr_municipality_40k3','lcr_municipality_40k4')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_lcr_municipality_50k <- rowSums(spillover_solar_df_final[, c('lcr_municipality_50k1', 'lcr_municipality_50k2')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_bndes_municipality_20k <- rowSums(spillover_solar_df_final[, c('bndes_municipality', 'bndes_municipality_20k2')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_bndes_municipality_40k <- rowSums(spillover_solar_df_final[, c('bndes_municipality_40k1', 'bndes_municipality_40k2','bndes_municipality_40k3','bndes_municipality_40k4')], na.rm = TRUE)
spillover_solar_df_final$solar_spill_bndes_municipality_50k <- rowSums(spillover_solar_df_final[, c('bndes_municipality_50k1', 'bndes_municipality_50k2')], na.rm = TRUE)

#removing unnecessary columns after sum
spillover_solar_df_final<-spillover_solar_df_final%>%
  select(-starts_with(c("new_mw_solar","bndes_municipality","lcr_municipality")))

spillover_solar_df_final<-spillover_solar_df_final%>%
  mutate(solar_spill_bndes_municipality_50k=if_else(solar_spill_bndes_municipality_50k>0,1,0))%>%
    mutate(solar_spill_bndes_municipality_40k=if_else(solar_spill_bndes_municipality_40k>0,1,0))%>%
  mutate(solar_spill_bndes_municipality_20k=if_else(solar_spill_bndes_municipality_20k>0,1,0))%>%
mutate(solar_spill_lcr_municipality_50k=if_else(solar_spill_lcr_municipality_50k>0,1,0))%>%
    mutate(solar_spill_lcr_municipality_40k=if_else(solar_spill_lcr_municipality_40k>0,1,0))%>%
  mutate(solar_spill_lcr_municipality_20k=if_else(solar_spill_lcr_municipality_20k>0,1,0))

# create 7 dplyr::lead variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_20k_pre1 =dplyr::lead(solar_spillover_20k_MW, n = 1, default=0),
         d_solar_20k_pre2 =dplyr::lead(solar_spillover_20k_MW, n = 2, default=0),
         d_solar_20k_pre3 =dplyr::lead(solar_spillover_20k_MW, n = 3, default=0),
         d_solar_20k_pre4 =dplyr::lead(solar_spillover_20k_MW, n = 4, default=0),
         d_solar_20k_pre5 =dplyr::lead(solar_spillover_20k_MW, n = 5, default=0),
         d_solar_20k_pre6 =dplyr::lead(solar_spillover_20k_MW, n = 6, default=0),
         d_solar_20k_pre7 =dplyr::lead(solar_spillover_20k_MW, n = 7, default=0))

spillover_solar_df_final$d_solar_20k_pre7_bin <- ave(spillover_solar_df_final$d_solar_20k_pre7,spillover_solar_df_final$id_municipio, FUN = revcumsum)

#CONTINUE HERE TOMORROW:
# create 7 dplyr::lag variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_20k_post1 =dplyr::lag(solar_spillover_20k_MW, n = 1, default=0),
         d_solar_20k_post2 =dplyr::lag(solar_spillover_20k_MW, n = 2, default=0),
         d_solar_20k_post3 =dplyr::lag(solar_spillover_20k_MW, n = 3, default=0),
         d_solar_20k_post4 =dplyr::lag(solar_spillover_20k_MW, n = 4, default=0),
         d_solar_20k_post5 =dplyr::lag(solar_spillover_20k_MW, n = 5, default=0),
         d_solar_20k_post6 =dplyr::lag(solar_spillover_20k_MW, n = 6, default=0),
         d_solar_20k_post7 =dplyr::lag(solar_spillover_20k_MW, n = 7, default=0))
spillover_solar_df_final$d_solar_20k_post3_bin <- ave(spillover_solar_df_final$d_solar_20k_post3,spillover_solar_df_final$id_municipio, FUN = cumsum)
spillover_solar_df_final$d_solar_20k_post4_bin <- ave(spillover_solar_df_final$d_solar_20k_post4,spillover_solar_df_final$id_municipio, FUN = cumsum)


#create a variable that indicates the year relative to the first introduction of solar and wind in the data period
spillover_solar_df_final<-spillover_solar_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_solar_df_final <- spillover_solar_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$solar_spillover_20k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_solar_20k = NA_real_)
    } else {
      .x %>% mutate(t_solar_20k = row_number() - switch_index)
    }
  })

# create 7 dplyr::lead variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_40k_pre1 =dplyr::lead(solar_spillover_40k_MW, n = 1, default=0),
         d_solar_40k_pre2 =dplyr::lead(solar_spillover_40k_MW, n = 2, default=0),
         d_solar_40k_pre3 =dplyr::lead(solar_spillover_40k_MW, n = 3, default=0),
         d_solar_40k_pre4 =dplyr::lead(solar_spillover_40k_MW, n = 4, default=0),
         d_solar_40k_pre5 =dplyr::lead(solar_spillover_40k_MW, n = 5, default=0),
         d_solar_40k_pre6 =dplyr::lead(solar_spillover_40k_MW, n = 6, default=0),
         d_solar_40k_pre7 =dplyr::lead(solar_spillover_40k_MW, n = 7, default=0))
spillover_solar_df_final$d_solar_40k_pre7_bin <- ave(spillover_solar_df_final$d_solar_40k_pre7,spillover_solar_df_final$id_municipio, FUN = revcumsum)

# create 7 dplyr::lag variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_40k_post1 =dplyr::lag(solar_spillover_40k_MW, n = 1, default=0),
         d_solar_40k_post2 =dplyr::lag(solar_spillover_40k_MW, n = 2, default=0),
         d_solar_40k_post3 =dplyr::lag(solar_spillover_40k_MW, n = 3, default=0),
         d_solar_40k_post4 =dplyr::lag(solar_spillover_40k_MW, n = 4, default=0),
         d_solar_40k_post5 =dplyr::lag(solar_spillover_40k_MW, n = 5, default=0),
         d_solar_40k_post6 =dplyr::lag(solar_spillover_40k_MW, n = 6, default=0),
         d_solar_40k_post7 =dplyr::lag(solar_spillover_40k_MW, n = 7, default=0))
spillover_solar_df_final$d_solar_40k_post3_bin <- ave(spillover_solar_df_final$d_solar_40k_post3,spillover_solar_df_final$id_municipio, FUN = cumsum)
spillover_solar_df_final$d_solar_40k_post4_bin <- ave(spillover_solar_df_final$d_solar_40k_post4,spillover_solar_df_final$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of solar and wind in the data period
spillover_solar_df_final<-spillover_solar_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_solar_df_final <- spillover_solar_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$solar_spillover_40k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_solar_40k = NA_real_)
    } else {
      .x %>% mutate(t_solar_40k = row_number() - switch_index)
    }
  })

# create 7 dplyr::lead variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_50k_pre1=dplyr::lead(solar_spillover_50k_MW, n = 1, default=0),
         d_solar_50k_pre2=dplyr::lead(solar_spillover_50k_MW, n = 2, default=0),
         d_solar_50k_pre3=dplyr::lead(solar_spillover_50k_MW, n = 3, default=0),
         d_solar_50k_pre4=dplyr::lead(solar_spillover_50k_MW, n = 4, default=0),
         d_solar_50k_pre5=dplyr::lead(solar_spillover_50k_MW, n = 5, default=0),
         d_solar_50k_pre6=dplyr::lead(solar_spillover_50k_MW, n = 6, default=0),
         d_solar_50k_pre7=dplyr::lead(solar_spillover_50k_MW, n = 7, default=0))
spillover_solar_df_final$d_solar_50k_pre7_bin <- ave(spillover_solar_df_final$d_solar_50k_pre7,spillover_solar_df_final$id_municipio, FUN = revcumsum)

# create 7 dplyr::lag variables
spillover_solar_df_final <- spillover_solar_df_final %>% 
  mutate(d_solar_50k_post1=dplyr::lag(solar_spillover_50k_MW, n = 1, default=0),
         d_solar_50k_post2=dplyr::lag(solar_spillover_50k_MW, n = 2, default=0),
         d_solar_50k_post3=dplyr::lag(solar_spillover_50k_MW, n = 3, default=0),
         d_solar_50k_post4=dplyr::lag(solar_spillover_50k_MW, n = 4, default=0),
         d_solar_50k_post5=dplyr::lag(solar_spillover_50k_MW, n = 5, default=0),
         d_solar_50k_post6=dplyr::lag(solar_spillover_50k_MW, n = 6, default=0),
         d_solar_50k_post7=dplyr::lag(solar_spillover_50k_MW, n = 7, default=0))
spillover_solar_df_final$d_solar_50k_post3_bin <- ave(spillover_solar_df_final$d_solar_50k_post3,spillover_solar_df_final$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of solar and wind in the data period
spillover_solar_df_final<-spillover_solar_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_solar_df_final <- spillover_solar_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$solar_spillover_50k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_solar_50k = NA_real_)
    } else {
      .x %>% mutate(t_solar_50k = row_number() - switch_index)
    }
  })

spillover_solar_df_final <- spillover_solar_df_final %>%
  select(id_municipio, ano, everything())

#merge remaining control variables back to the dataframe
merge<-annual_panel%>%select(-contains(c("mw", "MW", "d_solar","d_wind","t_","no_plants","mw_operation","plants","bndes")))

spillover_solar_df_final<-spillover_solar_df_final%>%
  left_join(merge, by=c("id_municipio","ano"))

saveRDS(spillover_solar_df_final, here("final","solar_spillover_final_noweights.RDS"))
```


14. create spillover data wind
```{r}
annual_panel<-readRDS(here("final","annual_panel_final_noweights.RDS"))
revcumsum <- function(x){
  x <- rev(cumsum(rev(x)))
}
library(sf)
library(tidyverse)
#create a dataframe with longitude and latitude of locations that have wind park larger 5 MW
 `%notin%` <- Negate(`%in%`)

mw_larger5_wind<-annual_panel%>%group_by(id_municipio)%>%filter(any(new_mw_wind>5) & ano>2004)%>%select(starts_with("new_mw"),ano, id_municipio,lon,lat)%>%distinct(id_municipio,lon,lat)
 

#create dataframe
 
all_mun<-annual_panel%>%distinct(id_municipio,lon,lat)%>%
  filter(id_municipio %notin% mw_larger5_wind$id_municipio)

# convert dataframes to sf objects
mw_larger5_wind <- st_as_sf(mw_larger5_wind, coords = c("lon", "lat"), crs = 4326)
all_mun <- st_as_sf(all_mun, coords = c("lon", "lat"), crs = 4326)

# Transform to Cartesian CRS for appropriate distance calculation
mw_larger5_wind <- st_transform(mw_larger5_wind, 3857)
all_mun <- st_transform(all_mun, 3857)

within_distance_list <- st_is_within_distance(all_mun, mw_larger5_wind, dist = set_units(20000, "meters"))

nearby_wind_list <- lapply(within_distance_list, function(x) {
  nearby_wind_ids <- mw_larger5_wind$id_municipio[unlist(x)]
  if (length(nearby_wind_ids) == 0) NA else nearby_wind_ids
})


names(nearby_wind_list) <- all_mun$id_municipio

nearby_wind_df <- tibble(id_municipio = names(nearby_wind_list), nearby_wind = nearby_wind_list)

max_len <- max(map_int(nearby_wind_df$nearby_wind, length), na.rm = TRUE)

nearby_wind_df <- nearby_wind_df %>%
  mutate(data = map(nearby_wind, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "wind_"))

#rename variables for final spillover dataset
nearby_wind_df<-nearby_wind_df%>%select(1,3,4)%>%
  rename(wind_spillover20k_1=wind_1, 
         wind_spillover20k_2=wind_2)

#Re do for 20-40km radius
# Find all municipalities within 40km
within_40km_list <- st_is_within_distance(all_mun, mw_larger5_wind, dist = set_units(40000, "meters"))

# Find all municipalities within 20km
within_20km_list <- st_is_within_distance(all_mun, mw_larger5_wind, dist = set_units(20000, "meters"))

# Determine municipalities that are more than 20km but less than or equal to 40km away
nearby_wind_list2 <- mapply(function(x, y) {
  nearby_wind_ids_40km <- mw_larger5_wind$id_municipio[unlist(x)]
  nearby_wind_ids_20km <- mw_larger5_wind$id_municipio[unlist(y)]
  nearby_wind_ids <- setdiff(nearby_wind_ids_40km, nearby_wind_ids_20km)
  if (length(nearby_wind_ids) == 0) NA else nearby_wind_ids
}, within_40km_list, within_20km_list)

names(nearby_wind_list2) <- all_mun$id_municipio

nearby_wind_df2 <- tibble(id_municipio = names(nearby_wind_list2), nearby_wind = nearby_wind_list2)

max_len <- max(map_int(nearby_wind_df2$nearby_wind, length), na.rm = TRUE)

nearby_wind_df2 <- nearby_wind_df2 %>%
  mutate(data = map(nearby_wind, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "wind_"))

#rename variables for final spillover dataset
nearby_wind_df2<-nearby_wind_df2%>%arrange(desc(nearby_wind))%>%
  select(1,3,4,5,6)%>%
  rename(wind_spillover40k_1=wind_1, 
         wind_spillover40k_2=wind_2,
         wind_spillover40k_3=wind_3,
         wind_spillover40k_4=wind_4)

#Re do for 40-50km radius
# Find all municipalities within 40km
within_50km_list <- st_is_within_distance(all_mun, mw_larger5_wind, dist = set_units(50000, "meters"))

# Find all municipalities within 40km
within_40km_list <- st_is_within_distance(all_mun, mw_larger5_wind, dist = set_units(40000, "meters"))

# Determine municipalities that are more than 40km but less than or equal to 50km away
nearby_wind_list3 <- mapply(function(x, y) {
  nearby_wind_ids_50km <- mw_larger5_wind$id_municipio[unlist(x)]
  nearby_wind_ids_40km <- mw_larger5_wind$id_municipio[unlist(y)]
  nearby_wind_ids <- setdiff(nearby_wind_ids_50km, nearby_wind_ids_40km)
  if (length(nearby_wind_ids) == 0) NA else nearby_wind_ids
}, within_50km_list, within_40km_list)

names(nearby_wind_list3) <- all_mun$id_municipio

nearby_wind_df3 <- tibble(id_municipio = names(nearby_wind_list3), nearby_wind = nearby_wind_list3)

max_len <- max(map_int(nearby_wind_df3$nearby_wind, length), na.rm = TRUE)

nearby_wind_df3 <- nearby_wind_df3 %>%
  mutate(data = map(nearby_wind, ~ `length<-`(.x, max_len))) %>%
  unnest_wider(data, names_sep = "_") %>%
  rename_at(vars(starts_with("data_")), ~ str_replace(., "data_", "wind_"))

#rename variables for final spillover dataset
nearby_wind_df3<-nearby_wind_df3%>%arrange(desc(nearby_wind))%>%
  select(1,3,4)%>%
  rename(wind_spillover50k_1=wind_1, 
         wind_spillover50k_2=wind_2)

years<-annual_panel%>%select(id_municipio, ano)


spillover_wind_df<-nearby_wind_df%>%
  left_join(nearby_wind_df2, by=("id_municipio"))%>%
  left_join(nearby_wind_df3, by=c("id_municipio"))
spillover_wind_df$id_municipio<-as.integer(spillover_wind_df$id_municipio)

spillover_wind_df<- spillover_wind_df%>%
  left_join(years, by=c("id_municipio"))

  
#getting the treatment assignment 
treatment<-annual_panel%>%select(id_municipio, ano, new_mw_wind, lcr_municipality, bndes_municipality)

spillover_wind_df_final<-spillover_wind_df%>%
  left_join(treatment, by=c("wind_spillover20k_1"="id_municipio","ano"), suffix=c("","_20k1"))%>%
  left_join(treatment, by=c("wind_spillover20k_2"="id_municipio","ano"), suffix=c("","_20k2"))%>%
  left_join(treatment, by=c("wind_spillover40k_1"="id_municipio","ano"), suffix=c("","_40k1"))%>%
  left_join(treatment, by=c("wind_spillover40k_2"="id_municipio","ano"), suffix=c("","_40k2"))%>%
  left_join(treatment, by=c("wind_spillover40k_3"="id_municipio","ano"), suffix=c("","_40k3"))%>%
  left_join(treatment, by=c("wind_spillover40k_4"="id_municipio","ano"), suffix=c("","_40k4"))%>%
  left_join(treatment, by=c("wind_spillover50k_1"="id_municipio","ano"), suffix=c("","_50k1"))%>%
  left_join(treatment, by=c("wind_spillover50k_2"="id_municipio","ano"), suffix=c("","_50k2"))

spillover_wind_df_final$wind_spillover_20k_MW <- rowSums(spillover_wind_df_final[, c('new_mw_wind', 'new_mw_wind_20k2')], na.rm = TRUE)
spillover_wind_df_final$wind_spillover_40k_MW <- rowSums(spillover_wind_df_final[, c('new_mw_wind_40k1', 'new_mw_wind_40k2','new_mw_wind_40k3','new_mw_wind_40k4')], na.rm = TRUE)
spillover_wind_df_final$wind_spillover_50k_MW <- rowSums(spillover_wind_df_final[, c('new_mw_wind_50k1', 'new_mw_wind_50k2')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_lcr_municipality_20k <- rowSums(spillover_wind_df_final[, c('lcr_municipality', 'lcr_municipality_20k2')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_lcr_municipality_40k <- rowSums(spillover_wind_df_final[, c('lcr_municipality_40k1', 'lcr_municipality_40k2','lcr_municipality_40k3','lcr_municipality_40k4')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_lcr_municipality_50k <- rowSums(spillover_wind_df_final[, c('lcr_municipality_50k1', 'lcr_municipality_50k2')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_bndes_municipality_20k <- rowSums(spillover_wind_df_final[, c('bndes_municipality', 'bndes_municipality_20k2')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_bndes_municipality_40k <- rowSums(spillover_wind_df_final[, c('bndes_municipality_40k1', 'bndes_municipality_40k2','bndes_municipality_40k3','bndes_municipality_40k4')], na.rm = TRUE)
spillover_wind_df_final$wind_spill_bndes_municipality_50k <- rowSums(spillover_wind_df_final[, c('bndes_municipality_50k1', 'bndes_municipality_50k2')], na.rm = TRUE)

#removing unnecessary columns after sum
spillover_wind_df_final<-spillover_wind_df_final%>%
  select(-starts_with(c("new_mw_wind","bndes_municipality","lcr_municipality")))

spillover_wind_df_final<-spillover_wind_df_final%>%
  mutate(wind_spill_bndes_municipality_50k=if_else(wind_spill_bndes_municipality_50k>0,1,0))%>%
    mutate(wind_spill_bndes_municipality_40k=if_else(wind_spill_bndes_municipality_40k>0,1,0))%>%
  mutate(wind_spill_bndes_municipality_20k=if_else(wind_spill_bndes_municipality_20k>0,1,0))%>%
mutate(wind_spill_lcr_municipality_50k=if_else(wind_spill_lcr_municipality_50k>0,1,0))%>%
    mutate(wind_spill_lcr_municipality_40k=if_else(wind_spill_lcr_municipality_40k>0,1,0))%>%
  mutate(wind_spill_lcr_municipality_20k=if_else(wind_spill_lcr_municipality_20k>0,1,0))

# create 7 dplyr::lead variables
spillover_wind_df_final <- spillover_wind_df_final %>% group_by(id_municipio)%>%
  mutate(d_wind_20k_pre1=dplyr::lead(wind_spillover_20k_MW, n = 1, default=0),
         d_wind_20k_pre2=dplyr::lead(wind_spillover_20k_MW, n = 2, default=0),
         d_wind_20k_pre3=dplyr::lead(wind_spillover_20k_MW, n = 3, default=0),
         d_wind_20k_pre4=dplyr::lead(wind_spillover_20k_MW, n = 4, default=0),
         d_wind_20k_pre5=dplyr::lead(wind_spillover_20k_MW, n = 5, default=0),
         d_wind_20k_pre6=dplyr::lead(wind_spillover_20k_MW, n = 6, default=0),
         d_wind_20k_pre7=dplyr::lead(wind_spillover_20k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_20k_pre7_bin <- ave(spillover_wind_df_final$d_wind_20k_pre7,spillover_wind_df_final$id_municipio, FUN = revcumsum)

# create 7 dplyr::lag variables
spillover_wind_df_final <- spillover_wind_df_final %>% 
  mutate(d_wind_20k_post1=dplyr::lag(wind_spillover_20k_MW, n = 1, default=0),
         d_wind_20k_post2=dplyr::lag(wind_spillover_20k_MW, n = 2, default=0),
         d_wind_20k_post3=dplyr::lag(wind_spillover_20k_MW, n = 3, default=0),
         d_wind_20k_post4=dplyr::lag(wind_spillover_20k_MW, n = 4, default=0),
         d_wind_20k_post5=dplyr::lag(wind_spillover_20k_MW, n = 5, default=0),
         d_wind_20k_post6=dplyr::lag(wind_spillover_20k_MW, n = 6, default=0),
         d_wind_20k_post7=dplyr::lag(wind_spillover_20k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_20k_post5_bin <- ave(spillover_wind_df_final$d_wind_20k_post5,spillover_wind_df_final$id_municipio, FUN = cumsum)
spillover_wind_df_final$d_wind_20k_post6_bin <- ave(spillover_wind_df_final$d_wind_20k_post6,spillover_wind_df_final$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of wind and wind in the data period
spillover_wind_df_final<-spillover_wind_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_wind_df_final <- spillover_wind_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$wind_spillover_20k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_wind = NA_real_)
    } else {
      .x %>% mutate(t_wind = row_number() - switch_index)
    }
  })

# create 7 dplyr::lead variables
spillover_wind_df_final <- spillover_wind_df_final %>% 
  mutate(d_wind_40k_pre1=dplyr::lead(wind_spillover_40k_MW, n = 1, default=0),
         d_wind_40k_pre2=dplyr::lead(wind_spillover_40k_MW, n = 2, default=0),
         d_wind_40k_pre3=dplyr::lead(wind_spillover_40k_MW, n = 3, default=0),
         d_wind_40k_pre4=dplyr::lead(wind_spillover_40k_MW, n = 4, default=0),
         d_wind_40k_pre5=dplyr::lead(wind_spillover_40k_MW, n = 5, default=0),
         d_wind_40k_pre6=dplyr::lead(wind_spillover_40k_MW, n = 6, default=0),
         d_wind_40k_pre7=dplyr::lead(wind_spillover_40k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_40k_pre7_bin <- ave(spillover_wind_df_final$d_wind_40k_pre7,spillover_wind_df_final$id_municipio, FUN = revcumsum)

# create 7 dplyr::lag variables
spillover_wind_df_final <- spillover_wind_df_final %>% 
  mutate(d_wind_40k_post1=dplyr::lag(wind_spillover_40k_MW, n = 1, default=0),
         d_wind_40k_post2=dplyr::lag(wind_spillover_40k_MW, n = 2, default=0),
         d_wind_40k_post3=dplyr::lag(wind_spillover_40k_MW, n = 3, default=0),
         d_wind_40k_post4=dplyr::lag(wind_spillover_40k_MW, n = 4, default=0),
         d_wind_40k_post5=dplyr::lag(wind_spillover_40k_MW, n = 5, default=0),
         d_wind_40k_post6=dplyr::lag(wind_spillover_40k_MW, n = 6, default=0),
         d_wind_40k_post7=dplyr::lag(wind_spillover_40k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_40k_post5_bin <- ave(spillover_wind_df_final$d_wind_40k_post5,spillover_wind_df_final$id_municipio, FUN = cumsum)
spillover_wind_df_final$d_wind_40k_post6_bin <- ave(spillover_wind_df_final$d_wind_40k_post6,spillover_wind_df_final$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of wind and wind in the data period
spillover_wind_df_final<-spillover_wind_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_wind_df_final <- spillover_wind_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$wind_spillover_40k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_wind = NA_real_)
    } else {
      .x %>% mutate(t_wind = row_number() - switch_index)
    }
  })

# create 7 dplyr::lead variables
spillover_wind_df_final <- spillover_wind_df_final %>% 
  mutate(d_wind_50k_pre1=dplyr::lead(wind_spillover_50k_MW, n = 1, default=0),
         d_wind_50k_pre2=dplyr::lead(wind_spillover_50k_MW, n = 2, default=0),
         d_wind_50k_pre3=dplyr::lead(wind_spillover_50k_MW, n = 3, default=0),
         d_wind_50k_pre4=dplyr::lead(wind_spillover_50k_MW, n = 4, default=0),
         d_wind_50k_pre5=dplyr::lead(wind_spillover_50k_MW, n = 5, default=0),
         d_wind_50k_pre6=dplyr::lead(wind_spillover_50k_MW, n = 6, default=0),
         d_wind_50k_pre7=dplyr::lead(wind_spillover_50k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_50k_pre7_bin <- ave(spillover_wind_df_final$d_wind_50k_pre7,spillover_wind_df_final$id_municipio, FUN = revcumsum)

# create 7 dplyr::lag variables
spillover_wind_df_final <- spillover_wind_df_final %>% 
  mutate(d_wind_50k_post1=dplyr::lag(wind_spillover_50k_MW, n = 1, default=0),
         d_wind_50k_post2=dplyr::lag(wind_spillover_50k_MW, n = 2, default=0),
         d_wind_50k_post3=dplyr::lag(wind_spillover_50k_MW, n = 3, default=0),
         d_wind_50k_post4=dplyr::lag(wind_spillover_50k_MW, n = 4, default=0),
         d_wind_50k_post5=dplyr::lag(wind_spillover_50k_MW, n = 5, default=0),
         d_wind_50k_post6=dplyr::lag(wind_spillover_50k_MW, n = 6, default=0),
         d_wind_50k_post7=dplyr::lag(wind_spillover_50k_MW, n = 7, default=0))
spillover_wind_df_final$d_wind_50k_post5_bin <- ave(spillover_wind_df_final$d_wind_50k_post5,spillover_wind_df_final$id_municipio, FUN = cumsum)

#create a variable that indicates the year relative to the first introduction of wind and wind in the data period
spillover_wind_df_final<-spillover_wind_df_final%>%arrange(id_municipio, ano)
detach("package:dplyr", unload = TRUE)
library(dplyr, warn.conflicts = FALSE)
spillover_wind_df_final <- spillover_wind_df_final %>%
  group_by(id_municipio) %>%
  group_modify(~ {
    switch_index <- which(.x$wind_spillover_50k_MW > 5)[1]
    if (is.na(switch_index)) {
      .x %>% mutate(t_wind = NA_real_)
    } else {
      .x %>% mutate(t_wind = row_number() - switch_index)
    }
  })

spillover_wind_df_final <- spillover_wind_df_final %>%
  select(id_municipio, ano, everything())

#merge remaining control variables back to the dataframe
merge<-annual_panel%>%select(-contains(c("mw", "MW", "d_wind","d_wind","t_","no_plants","mw_operation","plants","bndes")))

spillover_wind_df_final<-spillover_wind_df_final%>%
  left_join(merge, by=c("id_municipio","ano"))

saveRDS(spillover_wind_df_final, here("final","wind_spillover_final_noweights.RDS"))
```

